### 2024-03-31 paper/datasheet.qmd
update changes

---
title: "Datasheet for 'A dataset'"
author: 
  - Dong Jun Yoon
  - Yuean Wang
  - Yang Zhou
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
date: today
date-format: long
abstract: "The CES 2022 dataset, collected through an online survey by YouGov, encompasses 60,000 instances representing U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The instances are detailed and categorized by election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues. The dataset employs a matched random sampling methodology, with its representativeness validated through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing included sample matching, weighting, and vote validation, ensuring data quality and representativenes in order to avoid representative bias."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description
    - The Cooperative Election Study (CES) aims to study how Americans perceive and hold their representatives accountable during elections. Besides, the study also interested in understanding their voting behavior and how their behavior be affected by political geography and social context. They study the group by capturing mass data across most of legislative constituencies. CES aims to fill the gap of understanding the American electoral process by analyzing congressional elections and national surveys.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The Cooperative Election Study. It form 62 research teams and organizations. 
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - CES is supported by the National Science Foundation (NSF). Award #2148907 is the associated grant it has. The grantors involve numerous teams and collaborations.
4. *Any other comments?*
    - Based on real data, the guide provide a deep research of understanding American electoral behavior and different impacts of social contexts on voting aspect. It might provide implication for analyzing the trend of American elections.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances in CES 2022 dataset represent individual respondents attend in the survey, which designed to record various information related to electoral behaviour, political perspective and demographic characteristics. The The types of instances include election experience, contextual data, and demographic information.

2. *How many instances are there in total (of each type, if appropriate)?*
	- CES involves 60,000 cases. Those cases are based on the survey of adult pariticipants in 2022 fall.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- This dataset does not contain all possible instances. By contrast, it is more focus on drawn the sample from  a larger set of U.S. adult citizens.  
	  The sampling method used by YouGov in the CES involved a matched random sampling method. This method begins with a count of the target population, which for general population studies includes all adults and is usually counted through a comprehensive survey such as the American Community Survey. CES then draws a random sample from that target population, called the target sample.
	  The representativeness was validated by weighting procedures. This procedures aims to address any remaining imbalances among the matched sample. The sample is weighted to match the distribution of the frame across multiple demographic and political dimensions. The weighting process consists of two stages: entropy balancing, followed by iterative proportional fitting (tilting) of several key variables and their interactions.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- It consists demographic information, political opinions and behaviors, electoral experiences, voter validation an device and participation information. In terms of political opinions, it includes respondents' political affiliations, voting president and their positions on various policy issues and political figures.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Vote file miss matching might be one of missing information from individual instances. The CES relies on matching respondent to outside voter files. There might be some chance that name, address, or other details are mismatch with respondent, leading to mismatch between voting status and respondent.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- CES 2022 dataset does not buil up a explicitly model relationship between individual instances. Each instance in the CES dataset represents a single respondent's survey answers, capturing their demographic details, political views, voting behavior, and other relevant information.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Random measurement error might be one of potential errors. For example, some respondents provides wrong answer, which might lead to a number of respondents being incorrectly categorized.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- No, it does not link to external source. This dataset is mainly rely on survey collection of individual participants.Voter file matching might be an external consideration. Data for the CES 2022 study, including vote validation for all respondents, is archived and available at the Harvard University Dataverse. The restriction might be it does not include a specific restriction related to the TargetSmart database or other external resources used for voter file matching and verification are not detailed.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The CES 2022 dataset consists primarily of structured survey data collected from respondents about their political views, behaviors, and demographic information. Such data is generally not subject to legal privileges such as doctor-patient confidentiality or confidentiality of legal communications.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- In terms of Racial and Sexual Agreement, it might be offensive for the respondent, especially when the question design in a way that might present bias.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- There are lots of sub-population in the dataset. 
	1)Gender: The dataset categorizes respondents into "Man", "Woman", "Non-binary", and "Other", allowing for gender-based analyses.
	2)Race: The dataset categorizes respondents into "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other"
	3)Education: Respondents' highest education levels are detailed, ranging from no high school diploma ("No HS") to postgraduate degrees
	4)Political Affiliation: The dataset records respondents' party affiliation, including "Democrat", "Republican", and "Independent/Other".
	5)Age: The dataset provide age range  (e.g., 18-29, 30-44, 45-64, 65 and over).

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, all the dataset is anomymize.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- Yes, it includes race, sexual orientation, religious, political opinion, transgender status, health data and so on. For example, respondents are asked to answer their sexual orientation, with options including heterosexual/straight, lesbian/gay, bisexual, and others.
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data associated with each instance in the CES 2022 was primarily acquired through survey responses reported directly by the subjects. The survey was conducted online by YouGov and involved a methodology known as sample matching.The target population is first counted and then a representative sample is selected from a non-randomly selected group of respondents.
  - Regarding the data segments concerning voter validation, the process involved aligning individual entries with the TargetSmart database, which contains records of U.S. registered voters. This alignment aimed to confirm the accuracy of survey respondents' claims about their voter registration and their actual voting activity in both the primary and general elections of 2022.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The CES 2022 data was collected through an online survey conducted by YouGov. They employed  "sample matching" methodology, which fit with online access panels.This method identify available respondents who are very similar in terms of measured characteristics to each member of the target sample. The total distance is calculated as the weighted sum of these individual distances on all attributes, and the weights can be adjusted for variables that are important to the study. This approach allows matched samples to closely represent the characteristics of the target population.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The CES 2022 dataset's sampling strategy employed YouGov’s matched random sample methodology. 
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- . The CES involved 60 parties and research teams. The dataset does not provide specific details on how individuals be compensated.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Collected over two time frame: the first period is the pre-election data collection occurred from September 29 to November 8, 2022,and the second period is  post-election data was gathered from November 10 to December 15, 2022.The timeframe is relevant to survey participants about their opinions, voting intention in 2022 election.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	-  The dataset does not provide explicit details regarding any ethical review processes.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data for the 2022 Cooperative Election Study (CES) was collected directly from individuals through a survey conducted over the internet by YouGov.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	-Yes, because it is conducteddirectly from individuals through a survey conducted by YouGov over the internet. Cooperative Election Study (CES) or provide the exact language used in the notification. 
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The individuals participating in the 2022 Cooperative Election Study (CES) did provide their consent for data collection.The respondent will be asked if they agree to attend in the survey by inquired "Consent to participate: Do you agree to participate in the study?" The exact language used to request consent, is straightforward.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- The dataset does not provide specific information about whether individuals were given a mechanism to revoke their consent after agreeing to participate in the 2022 Cooperative Election Study (CES) or for certain uses of their data. 
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- The provided CES Guide 2022 document does not specifically describe conducting a data protection impact analysis. It emphasizes on on the methodology, sample matching, data collection, 
12. *Any other comments?*
	- No

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, CES involves some data preprocessing, cleaning, and labeling to make sure the quality of the data. The descriptions have been included in the sampling methodology, matching procedures, and weighting processes. CES done 3 things, which are sampling and sample matching, weighting, and vote validation.To be more specific, in order to correct for any residual imbalances between the matched sample and the target population, the CES data was weight through 2 steps. First, using entropy balancing to match the distributions of the frame on key demographic variables (age, gender, education, race, etc.), and then using iterative proportional fitting ("raking") on additional variables (like voter registration status and 2020 Presidential vote choice) to further refine the representativeness of the sample. 
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The CES Guide 2022 does not explicitly mention whether the "raw" data save in addition to the preprocessed/cleaned/labeled data.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- No.
4. *Any other comments?*
	- No.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The CES Guide 2022 does not provide specific examples of tasks for which the dataset has already been used.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The CES Guide 2022 does not explicitly mention a repository that links to paper.
3. *What (other) tasks could the dataset be used for?*
	- There are multiple task that the dataset can be used for. For example, to analyze voting behavior and study the impact of socioeconomic factor on political outcome.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Yes.The methodology section details efforts to create a representative sample and address potential biases through sample matching, weighting, and vote validation in order to avoid representation bias.The customer can ensure all research complies with applicable laws, ethical standards, and best practices for data privacy and protection.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No.
6. *Any other comments?*
	- No.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, it will. It indicated that the data for the Cooperative Election Study (CES) 2022 is available at the Harvard University Dataverse. This can be seem as the dataset is accessible to third parties outside of the institutions directly involved in the creation of the dataset, such as Harvard University and YouGov.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The Cooperative Election Study (CES) 2022 will be distributed through the Harvard University Dataverse. This distribution method ensures that the dataset is accessible for academic and research purposes. The DOI for the Cooperative Election Study Common Content 2022 is https://doi.org/10.7910/DVN/PR4L8P, 
3. *When will the dataset be distributed?*
	- Dataset is distributed in two period: first, on March 20, 2023. It included the CES 2022 Common Content, which is the data collected that is common across all participating research teams.The second period is on September 8, 2023, it included vote validation for all respondents, enhancing the dataset's utility for electoral research by verifying the voting behavior reported by the survey participants.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- No.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset for the CES 2022 is maintained and hosted by the Harvard University Dataverse.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- People can directly contact The Harvard University Dataverse platform.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The guide does not provide detail information about update.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The CES Guide 2022 does not provide specific information regarding limits on the retention of data associated with the instances.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- The guide does not discuss about the policies regarding the support, hosting, or maintenance of older versions of the dataset.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- The guide does not include a explicit mechanism for others to extend to the dataset.
8. *Any other comments?*
	- No

\newpage

# References

### 2024-03-31 paper/paper.qmd
update changes

---
title: "Demographic Groups with Stronger Biden Support in the Election Races'"
author: 
  - Yang Zhou
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-State.git >"
date: today
date-format: long
abstract: "This paper explores the relationship between voting preferences and the predictors of education, income, and personal gun ownership in the United States through analyzing 2022 US election database. By examining data from Cooperative Election Study, we identify clear patterns indicating that higher income are more likely to vote for Biden. Besides, the higher personal gun ownership will also significantly increase the likelihood of voting for Biden. By contrast, the people with higher education level show less probability to vote for Biden. Our findings underscore the critical impact of socio-economic status and personal security concerns on electoral outcomes, shedding light on the underlying dynamics that shape voter behavior in contemporary American politics. Ultimately, this research contributes to our understanding of the complex factors that drive electoral decisions, offering valuable insights for policymakers, political strategists, and citizens aiming to foster more informed and equitable democratic processes."

format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(here)
library(modelsummary)
library(knitr)
library(kableExtra)
library(readr)
library(ggplot2)
```

# Introduction
The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu. The Cooperative Election Study (CES) serves as a crucial platform for understanding the complexities of American electoral systems. This paper delves into the findings of the 2022 CES, which aimed to provide insights into voter behavior, perceptions of electoral experiences, and the broader socio-political milieu shaping democratic governance. With a focus on exploring how Americans vote, perceive their electoral experiences, and navigate the political climate, the CES helps us in understanding the electoral outcomes in the United States.

The Cooperative Election Study (CES) addressed gaps in understanding voter behavior by employing a multifaceted approach involving 60,000 cases and 60 research teams. Their methods included pre-election surveys and post-election assessments, providing detailed insights into American elections. Pre-election surveys were filled out on the spot between September 29 and November 8. The Post-election campaigning frenzy took place between November 10 and December 15. For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team. Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content. Every one of the sixty teams bought a 1,000-person survey. Every case was chosen online, and YouGov created a corresponding random sample for this investigation. The first data release happened on March 20, 2023. The Harvard University database contains archived and accessible data from this investigation. Vote verification is included in data release 2 for all respondents. The study on CES 2022 is still under progress. Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation. The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005. Understanding these findings is crucial for policymakers, researchers, and citizens, as they shed light on the complexities of democracy and provide insights to strengthen democratic institutions. This paper aims to dive deeper into the CES findings, analyzing their implications for the future of American democracy.

Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}. Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes. It will talk about how the model is set up and model justification. In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model. Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language `R`[@citeR] . The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].

# Data {#sec-data}

## Source and Methodology
The 2022 Cooperative Election Study (CES) [@main_data] involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data. These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.

## Sampling and Sampling Matching
The CES 2022 dataset is a sample of adult U.S. citizens, taken from a considerably larger population, rather than an exhaustive list of all possible cases in the target population. The sample was deliberately created to be a true reflection of the population of the United States and to capture the variations among the different legislative districts for in-depth examination in the majority of states.
Through the Internet, YouGov [@yougov] conducted the CES 2022 survey. 60,000 adults were interviewed between September and November 2022 (pre-election data) and November and December 2022 (post-election data) for the Common Opinion. The YouGov matching approach for random sampling was used. YouGov employed the matched random sampling method at CES among other sampling techniques. The first step in this process is to count the target population, which in the case of general population research consists of all adults. This is typically done by using an extensive survey such as the American Community Survey. The target sample is then selected at random by CES from this target population. 
However, because it is frequently impractical to make direct contact with these individuals, a matching sample is chosen from among selectable respondents who share the same characteristics as the target sample. This selection process is carried out based on a multitude of attributes available in the voter and consumer databases.

## Weightening
A weighting process is used to account for any residual imbalances between the matched samples, therefore rigorously verifying the representativeness of CES samples. The weighting of the sample was adjusted to align with the framework's distribution along several demographic and political aspects. Entropy balancing and iterative proportional fitting (sequencing) of multiple important variables and their interactions comprise the first stage of the weighting process. The sample is also thought to be representative of every state for the survey's common content and takes into account changes for statewide political races.
There are two steps involved in selecting samples when utilizing the matching approach. First, select a sample at random from the intended audience. This sample is known as the target sample. The process of choosing a "representative" sample from a non-random sample of responders is known as sample matching. Although it works well for Web access panels, it may also be applied to other survey kinds, such phone surveys. The target population is enumerated before sample matching begins. All adults are the target group for general population studies, and they can be counted using either a top-notch survey like the American Community Survey or the decennial Census. This is referred to as a sampling frame in other contexts, although unlike traditional sampling, the sample is not taken out of the frame. 
Using traditional sampling, participants in the study are chosen at random from a framework for sampling. Because not every person in the framework has access to contact information, particularly email addresses, and because declining to participate would raise the expense of sampling in this manner, it could not be practical or cost-effective.

## Vote Vaildation
The CES incorporated vote validation to verify the accuracy of respondents’ reported voting behaviors. Individual records were matched to the TargetSmart database of registered voters, and only records with a high level of confidence were considered matched. This process helped identify respondents who voted in the 2022 General and Primary Elections, as well as their modes of voting (e.g., absentee, early, mail, etc.). This validation step is crucial for analyses focused on voting behaviors and ensures that the CES data reflects actual voter participation.

These methodologies indicate a comprehensive approach to data preprocessing, cleaning, and labeling within the CES 2022, aiming to enhance the accuracy, reliability, and representativeness of the survey data.

## Variables
```{r}
#| label: fig-variables
#| fig-cap: Brief summary of variables types
#| echo: false
#| warning: false
#| message: false

ces2022 <-  read_csv(file = here::here("data/raw_datas/raw_datas.csv"))
    col_types =
      cols(
        "votereg" = col_integer(),
        "presvote20post" = col_integer(),
        "gender" = col_integer(),
        "race" = col_integer()
      )

ces2022 |> slice_head(n = 10) |>
  kable(booktabs = TRUE, caption = "Brief summary of variables types") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and race
#| echo: false
#| warning: false
#| message: false

library(ggplot2)
library(readr)
library(here)

ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))

ggplot(data = ces2022, aes(x = race, fill = voted_for)) +
  geom_bar(position = "dodge") +  
  geom_text(
    aes(label = ..count..),
    stat = 'count',
    position = position_dodge(width = 0.9),
    vjust = -0.25,
    color = "black",
    size = 3  
  ) +
  facet_wrap(facets = vars(gender4)) +
  theme_minimal(base_size = 14) +  
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +  
  scale_fill_brewer(palette = "Set1") +
  theme(
    legend.position = "bottom",
    strip.text = element_text(size = 12)  
  )

```
   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` to access the CES. We select and save the data that we are most care about, which are `votereg`, `presvote20post`, `race`, and `gender4`. `votereg` represent the voter registration status. To be more specific, whether they are registered to vote or not. `presvote20post` records the president that voter select in the election of 2020. “race" describe the voter's raical or ethnic group, and `gender4` refer to the gender of voters.
  However, when we access the raw data, there are some variables that we are not interested in. Therefore, we use the codebook to delve into the details. We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020. We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump. We use `tidyverse` [@tidyverse] to filter to the voters that we care about and label them with meaningful title. In addition，CES also provide the information for the gender of the voter. However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman. Therefore, we filter the gender by using `tidyverse` [@tidyverse]. When the variable `gender` is 1, this indicates "man", but we rename all "man" to "male". When the variable "gender" is 2, it refers to "woman". We also rename all "woman" to "female". Finally, the codebook also define different `race` from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other. We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
  To better understand the raw data, a summary table @fig-variables had been drawn in order to provide more details for each variables, explaining the variables we select. We select race and gender as the key variables that related to voter behavior. In @fig-vote, we can find the support data for both Biden and Trump based on the variables of gender and race.

## Measurements 
The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender and race), political affiliations, and opinions on various policy issues. This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S. electorate. The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.

To better understand the American election and its voting system that occurred in 2022, we need to follow these steps:

**Define the Population:** The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022. Individual respondents participate in the survey, which is designed to record various information related to electoral behavior, political perspectives, and demographic characteristics.

**Gather Data:** Acquire information regarding the total number of confirmed survey cases. This dataset should include various factors such as,  election experiences, contextual data, demographic details, political affiliations, and viewpoints on diverse policy matters.

**Determine the Time Period:** Specify the time frame to calculate when the survey object was collected. The timeframe is relevant to survey participants about their opinions, voting intentions in the 2022 election. The first period is the pre-election data collection that occurred from September 29 to November 8, 2022, and the second period is post- election data gathered from November 10 to December 15, 2022.

**Calculate the Case:** Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.

# Model {#sec-model}
## Model set-up

Define $y_i$ is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\mbox{gender}_i$ is the gender of the respondent and $\mbox{race}_i$ is the race of the respondent.  
We could estimate the parameters using `stan_glm()`. Note that the model is a generally accepted short-hand.  In practice rstanarm converts categorical variables into a series of indicator variables and there are multiple coefficients estimated. In the interest of run-time we will randomly sample 500 observations and fit the model on that, rather than the full dataset.

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{gender}_i +\beta_2 \times \mbox{education}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5)\\
\beta_1 &\sim \mbox{Normal}(0, 2.5)\\
\beta_2 &\sim \mbox{Normal}(0. 2.5)
\end{align}

In `R` [@citeR], we run a logistic regression model in a Bayesian framework by using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm` in order to specific prior probability distributions for each of the parameters in the model. Logistic regression model is used to identify the correlation or relationship between some predictor variables and a outcome variable [@rohan], which is best fit with our research because we aim to identify the relationship between gender and race and support of Biden.

Through feature selection, the influence of redundant features and noise features is reduced, and the generalization ability of the model is improved. By means of L1 regularization and L2 regularization, the complexity of the model is limited and overfitting is prevented. By integrating the results of multiple classifiers, the accuracy and robustness of the model are improved. By changing the structure of the model, such as increasing the depth of the network, increasing the hidden layer and changing the activation function, the expressibility of the model is improved. By expanding, rotating and scaling the data, the diversity of the data is increased and the generalization ability of the model is improved.

## Model justification

We expect a positive relationship between the size of the wings and time spent aloft. Logistic regression models learn and predict very quickly
Fast, because logistic regression is a linear model, its decision function is a very simple linear function, so its computational complexity is low. Logistic regression model is easy to interpret, and the coefficient of the model can give the degree of influence of each feature on the model. This can be used in real business applications to help decision makers better understand the model's predictions. In addition, logistic regression models can handle large scale data well, because logistic regression models only need to dimension a small number of parameters to adapt well to a large number of parameters.

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results {#sec-results}
Our results are summarized in @tbl-model-summary-tableLogistic, regression is a common classification algorithm used to predict binary classification problems. In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function. When interpreting the results of logistic regression models. Logistic regression models can provide coefficients (or weights) for each feature variable that represent the relative importance of the feature. The positive and negative symbols of the coefficient can tell us whether the feature has positive or negative influence on the target category, and the absolute value of the coefficient can map the importance of the feature to the target category.

In this paper, we performed a logistic regression model from our cleaned dataset, which analysis 500 observations. Our focus of this paper was relationship of presidential candidate voted by individuals between the races (raceBlack, raceHispanic, raceMiddle Eastern, raceNative American, raceOther, raceTwo or more races, raceWhite) and the reference group, raceAsian.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

us_political_preferences <-
  readRDS(file = here::here("model/first_model.rds"))
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-model-summary-table
#| tbl-cap: "Explanatory models of political preferences based on gender and race (n = 500)"

modelsummary(
  list(
    "Support Biden" = us_political_preferences
  ),
  statistic = "mad"
)

```
The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump. When the coefficient values are negative, which means the voters decrease their support in Biden. Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden.

From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
# Discussion {#sec-Discussion}

## Findings
In this paper, the 2022 Cooperative Election Study (CES) was used for understanding the complexities of American electoral systems which was discussed in Section 2. In section 3, we applied a Bayesian logistic regression model to know if a person is likely to support Biden, based on their gender, race, and education status. In section 4, we discussed the summarization of the major results based on the research we did in Section 2 and 3. Summarization of our major results:

1.Males are less likely to support Biden than Females,women most likely to vote for Biden,
2.Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.

Throughout the discussion part, we will now provide detailed points of our results in the following sections.

## Males are less likely to support Biden than Females, women most likely to vote for Biden.

Based on the analysis of @fig-vote, located under 2.6 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2). Throughout most of the race, 1 consistently has fewer votes than 2. Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy. This trend is very recognizable based on research: women are registered to vote in the U.S. at higher rates than men. In recent years, the number of women registered to vote in the U.S. has typically been about 10 million more than the number of men registered to vote. In every presidential election since 1980, the proportion of eligible female adults who voted has exceeded the proportion of eligible male adults who voted. In all presidential elections prior to 1980, the voter turnout rate for women was lower than the rate for men. The number of female voters has exceeded the number of male voters in every presidential election since 1964.

## Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.

Based on the analysis of @fig-vote, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, and Asian individuals are more likely to vote and show support for Biden. In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races. For example, Hispanic individuals have a total vote of 2481 individuals for Biden, however only 1210 individuals support and vote for Trump. This same trend can also be observed in races such as Middle Eastern, Hispanic, and Asian individuals. Additionally, in recent elections, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters. The gender gap in voter turnout rates is the largest for Black voters. In @tbl-model-summary-tableLogistic of our paper, we observe a negative coefficient for black people (−1.030) in support for Biden, indicating that Black people are displaying less support and fewer votes for Biden. The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump. When the coefficient values are negative, which means the voters decrease their support in Biden. Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden. Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s. Among Asian American/Pacific Islander voters, there is no consistent gender gap in voter turnout.

## Application of Logistic Regression 
Logistic regression is also known as generalized linear regression model, and its form is basically the same as that of linear regression model. The biggest difference lies in their different dependent variables. If it is continuous, it is multiple linear regression. If it is a binomial distribution, it is Logistic regression.
Although Logistic regression has the name "regression", it is actually a classification method, mainly used for binary classification problems (that is, there are only two outputs, each representing two categories), but also can handle multiple classification problems.
Linear regression is used to predict continuous variables, whose value range is (- ", + "), while logistic regression model is used to predict categories. For example, using logistic regression model to predict whether an item belongs to class A or Class B essentially predicts the probability that the item belongs to class A or class B, and the value range of probability is 0~1. Therefore, it is not possible to predict the probability directly with the linear regression equation, which involves the Sigmoid function, which converts the values of the range (-∞, +∞) to the range (0,1).

## Linear Regression Model
In summary, the essence of logistic regression model is to transform the linear regression model Q through a nonlinear Sigmoid function to obtain a probability value between 0 and 1. For binary classification problem (classification 0 and 1), the probability of predicting the classification as 1(or the classification with a larger value in the binary classification) can be calculated using the formula shown below. df has a total of about 7000 groups of historical data, of which about 2000 groups are lost customers, about 5000 groups are not lost customers will "whether to lose" as the target variable, other fields as characteristic variables, through some basic information and transaction records of a customer to predict whether he will lose, or judge the probability of loss.

## Model Building
The training set is used to train the data and build the model, and the test set is used to check the effect of the model built after training. The purpose of dividing the training set and the test set is to evaluate the model, and to optimize the model through the test set. Dividing the training set and the test set is also, in part, to check for overfitting of the model.

## Weaknesses and Next Steps

Logistic regression can only deal with linearly separable problems, and for nonlinear separable data, logistic regression will be poor. Logistic regression is sensitive to outliers, and if there are outliers in the data, the effect of logistic regression may be affected. Finally, logistic regression can usually only handle binary classification problems, and for multi-classification problems, some additional processing is required. If the sample size is insufficient or the features are too complex, logistic regression is prone to overfitting.

\newpage

# References {#sec-Reference}

### 2024-03-31 paper/paper.qmd
update change

@@
 Ultimately, this research contributes to our understanding of the complex factors that drive electoral decisions, offering valuable insights for policymakers, political strategists, and citizens aiming to foster more informed and equitable democratic processes."
-
 format: pdf
@@
 # Introduction
-The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu.
-The Cooperative Election Study (CES) serves as a crucial platform for understanding the complexities of American electoral systems.
-This paper delves into the findings of the 2022 CES, which aimed to provide insights into voter behavior, perceptions of electoral experiences, and the broader socio-political milieu shaping democratic governance.
-With a focus on exploring how Americans vote, perceive their electoral experiences, and navigate the political climate, the CES helps us in understanding the electoral outcomes in the United States.
+2020 United States Presidential Election stood as an important political event, reflecting societal divisions and highlighting the influence of various demographic factors on voting behavior.
+This election, which culminated in the victory of Joe Biden over incumbent Donald Trump, has spurred a renewed interest in understanding the dynamics of voter preferences and the underlying factors that drive electoral decisions.
+Our study aims to dissect the relationship between voters' educational background, income levels, personal gun ownership, and their voting preferences, employing logistic regression analysis to reveal the potential associations between different factors.
 
-The Cooperative Election Study (CES) addressed gaps in understanding voter behavior by employing a multifaceted approach involving 60,000 cases and 60 research teams.
-Their methods included pre-election surveys and post-election assessments, providing detailed insights into American elections.
-Pre-election surveys were filled out on the spot between September 29 and November 8.
-The Post-election campaigning frenzy took place between November 10 and December 15.
-For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team.
-Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content.
-Every one of the sixty teams bought a 1,000-person survey.
-Every case was chosen online, and YouGov created a corresponding random sample for this investigation.
-The first data release happened on March 20, 2023.
-The Harvard University database contains archived and accessible data from this investigation.
-Vote verification is included in data release 2 for all respondents.
-The study on CES 2022 is still under progress.
-Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation.
-The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.
-Understanding these findings is crucial for policymakers, researchers, and citizens, as they shed light on the complexities of democracy and provide insights to strengthen democratic institutions.
-This paper aims to dive deeper into the CES findings, analyzing their implications for the future of American democracy.
+The Cooperative Election Study (CES)conduct a throughout survey encompassing a wide range of voter demographics and attitudes.CES collaborate with 60 researches teams to assembles sample comprising 60,000 cases.
+The cases are based on the survey of adult pariticipants in 2022 fall.
+YouGov was commissioned to help the teams to conduct national sample surbey.
+They conducted the survey before and after elections.
+The first round survey were completed from September 29 to November 8, 2022 and the second period is gathered from November 10 to December 15, 2022.
+By offering an throughout views to different constituencies, voter demographics and voter behaviors, CES reveals the complexity of electoral behavior and voter demographics.
+By understanding voter behaviors,, we gain valuable insights that pave the way for refining and advancing democratic practices.
 
-Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}.
-Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes.
-It will talk about how the model is set up and model justification.
-In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model.
-Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
-This paper uses the programming language `R`[@citeR] .
-The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].
+In addition, by leveraging data from the 2022 CES, this paper delves into how variables such as education, income, and gun ownership serve as predictors for electoral choices, specifically the likelihood of voting for Biden or Trump.
+This analysis not only reveal the individual impact of these factors but also contributes to a broader understanding of the socio-economic and cultural impact of American electoral behavior.
+
+Based on our model, I found that individuals with higher incomes demonstrate a greater propensity to vote for Biden.
+Additionally, elevated levels of personal gun ownership significantly correlate with an increased likelihood of supporting Biden.
+Conversely, individuals possessing higher levels of education exhibit a reduced probability of voting for Biden.
+
+To be more specific, this paper is structured as follow: in {#sec-data}, I will introduce the data variable and how the data is used for the overall analysis.Visualization would also be included.
+In {#sec-model}, I will set up the model to predict the relationship between the predictors and electoral outcomes.
+Model justification will provide a rationale for selecting logitics model.
+{#sec-results} is focused on explain the result of the model.
+Lastly, {#sec-Discussion} provides a discussion on what we found in the model.
+I will also talk about the weakness of this paper along with the further study on this topic.
+
+I will uses the programming language `R`[@citeR] to analyze the data.
+`dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm] will help me in the model and visualization part.
 

### 2024-03-31 scripts/04-model.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models the relationship between voting preference and predictors of ducation, income, and personal gun ownership by logistic regression. It will implement with Bayesian methods via the rstanarm package.
+# Purpose: Models the relationship between voting preference and predictors of education, income, and personal gun ownership by logistic regression. It will implement with Bayesian methods via the rstanarm package.
 # Author: Yang Zhou
 # Date: 30 March 2024
 # Contact: cocoyang.zhou@mail.utoronto.ca

### 2024-04-01 paper/paper.qmd
upload change

@@
 ---
-title: "Demographic Groups with Stronger Biden Support in the Election Races'"
+title: "Demographic Groups with Stronger Biden Support in the Election Race'"
 author: 
@@
 ## Source and Methodology
-The 2022 Cooperative Election Study (CES) [@main_data] involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data.
-These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.
 
 ## Sampling and Sampling Matching
-The CES 2022 dataset is a sample of adult U.S.
-citizens, taken from a considerably larger population, rather than an exhaustive list of all possible cases in the target population.
-The sample was deliberately created to be a true reflection of the population of the United States and to capture the variations among the different legislative districts for in-depth examination in the majority of states.
-Through the Internet, YouGov [@yougov] conducted the CES 2022 survey.
-60,000 adults were interviewed between September and November 2022 (pre-election data) and November and December 2022 (post-election data) for the Common Opinion.
-The YouGov matching approach for random sampling was used.
-YouGov employed the matched random sampling method at CES among other sampling techniques.
-The first step in this process is to count the target population, which in the case of general population research consists of all adults.
-This is typically done by using an extensive survey such as the American Community Survey.
-The target sample is then selected at random by CES from this target population.
-However, because it is frequently impractical to make direct contact with these individuals, a matching sample is chosen from among selectable respondents who share the same characteristics as the target sample.
-This selection process is carried out based on a multitude of attributes available in the voter and consumer databases.
 
 ## Weightening
-A weighting process is used to account for any residual imbalances between the matched samples, therefore rigorously verifying the representativeness of CES samples.
-The weighting of the sample was adjusted to align with the framework's distribution along several demographic and political aspects.
-Entropy balancing and iterative proportional fitting (sequencing) of multiple important variables and their interactions comprise the first stage of the weighting process.
-The sample is also thought to be representative of every state for the survey's common content and takes into account changes for statewide political races.
-There are two steps involved in selecting samples when utilizing the matching approach.
-First, select a sample at random from the intended audience.
-This sample is known as the target sample.
-The process of choosing a "representative" sample from a non-random sample of responders is known as sample matching.
-Although it works well for Web access panels, it may also be applied to other survey kinds, such phone surveys.
-The target population is enumerated before sample matching begins.
-All adults are the target group for general population studies, and they can be counted using either a top-notch survey like the American Community Survey or the decennial Census.
-This is referred to as a sampling frame in other contexts, although unlike traditional sampling, the sample is not taken out of the frame.
-Using traditional sampling, participants in the study are chosen at random from a framework for sampling.
-Because not every person in the framework has access to contact information, particularly email addresses, and because declining to participate would raise the expense of sampling in this manner, it could not be practical or cost-effective.
 
 ## Vote Vaildation
-The CES incorporated vote validation to verify the accuracy of respondents’ reported voting behaviors.
-Individual records were matched to the TargetSmart database of registered voters, and only records with a high level of confidence were considered matched.
-This process helped identify respondents who voted in the 2022 General and Primary Elections, as well as their modes of voting (e.g., absentee, early, mail, etc.).
-This validation step is crucial for analyses focused on voting behaviors and ensures that the CES data reflects actual voter participation.
-
-These methodologies indicate a comprehensive approach to data preprocessing, cleaning, and labeling within the CES 2022, aiming to enhance the accuracy, reliability, and representativeness of the survey data.
 
@@
         "presvote20post" = col_integer(),
-        "gender" = col_integer(),
-        "race" = col_integer()
+        "educ" = col_integer(),
+        "faminc_new" = col_integer(),
+        "gunown" = col_integer()
       )
@@
 
-ggplot(data = ces2022, aes(x = race, fill = voted_for)) +
+ggplot(data = ces2022, aes(x = educ, fill = voted_for)) +
   geom_bar(position = "dodge") +  
@@
     color = "black",
-    size = 3  
+    size = 2.5  
   ) +
-  facet_wrap(facets = vars(gender4)) +
+  facet_wrap(facets = vars(income_group)) +
   theme_minimal(base_size = 14) +  
   labs(
-    x = "Race",
+    x = "Education",
     y = "Number of respondents",
@@
   )
-
 ```
-   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` to access the CES.
-We select and save the data that we are most care about, which are `votereg`, `presvote20post`, `race`, and `gender4`.
-`votereg` represent the voter registration status.
-To be more specific, whether they are registered to vote or not.
-`presvote20post` records the president that voter select in the election of 2020.
-“race" describe the voter's raical or ethnic group, and `gender4` refer to the gender of voters.
-  However, when we access the raw data, there are some variables that we are not interested in.
-Therefore, we use the codebook to delve into the details.
-We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020.
-We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump.
-We use `tidyverse` [@tidyverse] to filter to the voters that we care about and label them with meaningful title.
-In addition，CES also provide the information for the gender of the voter.
-However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman.
-Therefore, we filter the gender by using `tidyverse` [@tidyverse].
-When the variable `gender` is 1, this indicates "man", but we rename all "man" to "male".
-When the variable "gender" is 2, it refers to "woman".
-We also rename all "woman" to "female".
-Finally, the codebook also define different `race` from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other.
-We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
-  To better understand the raw data, a summary table @fig-variables had been drawn in order to provide more details for each variables, explaining the variables we select.
-We select race and gender as the key variables that related to voter behavior.
-In @fig-vote, we can find the support data for both Biden and Trump based on the variables of gender and race.
 
 ## Measurements
-The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S.
-adult citizens' electoral behaviors, political opinions, and demographic characteristics.
-The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender and race), political affiliations, and opinions on various policy issues.
-This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S.
-electorate.
-The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting.
-Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.
-
-To better understand the American election and its voting system that occurred in 2022, we need to follow these steps:
-
-**Define the Population:** The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022.
-Individual respondents participate in the survey, which is designed to record various information related to electoral behavior, political perspectives, and demographic characteristics.
-
-**Gather Data:** Acquire information regarding the total number of confirmed survey cases.
-This dataset should include various factors such as,  election experiences, contextual data, demographic details, political affiliations, and viewpoints on diverse policy matters.
-
-**Determine the Time Period:** Specify the time frame to calculate when the survey object was collected.
-The timeframe is relevant to survey participants about their opinions, voting intentions in the 2022 election.
-The first period is the pre-election data collection that occurred from September 29 to November 8, 2022, and the second period is post- election data gathered from November 10 to December 15, 2022.
-
-**Calculate the Case:** Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.
 
@@
 Define $y_i$ is the political preference of the respondent and equal to 1 if Biden and 0 if Trump.
-Then $\mbox{gender}_i$ is the gender of the respondent and $\mbox{race}_i$ is the race of the respondent.
-We could estimate the parameters using `stan_glm()`.
-Note that the model is a generally accepted short-hand.
-In practice rstanarm converts categorical variables into a series of indicator variables and there are multiple coefficients estimated.
-In the interest of run-time we will randomly sample 500 observations and fit the model on that, rather than the full dataset.
+Then $\mbox{education}_i$ is education level of the respondent and $\mbox{income}_i$ is the income of the respondent.
+
+The parameters can be derived utilizing the `stan_glm()` function.
+Practically, `rstanarm` transforms categorical variables into a set of binary indicators, leading to the estimation of numerous coefficients.
+To optimize computational efficiency, we will select a random subset of 500 data points for model fitting instead of using the entire dataset.
 
@@
 y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
-\mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{gender}_i +\beta_2 \times \mbox{education}_i\\
+\mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{education}_i +\beta_2 \times \mbox{income}_i\\
 \beta_0 &\sim \mbox{Normal}(0, 2.5)\\
@@
 
-In `R` [@citeR], we run a logistic regression model in a Bayesian framework by using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm` in order to specific prior probability distributions for each of the parameters in the model.
-Logistic regression model is used to identify the correlation or relationship between some predictor variables and a outcome variable [@rohan], which is best fit with our research because we aim to identify the relationship between gender and race and support of Biden.
-
-Through feature selection, the influence of redundant features and noise features is reduced, and the generalization ability of the model is improved.
-By means of L1 regularization and L2 regularization, the complexity of the model is limited and overfitting is prevented.
-By integrating the results of multiple classifiers, the accuracy and robustness of the model are improved.
-By changing the structure of the model, such as increasing the depth of the network, increasing the hidden layer and changing the activation function, the expressibility of the model is improved.
-By expanding, rotating and scaling the data, the diversity of the data is increased and the generalization ability of the model is improved.
-
 ## Model justification
 
-We expect a positive relationship between the size of the wings and time spent aloft. Logistic regression models learn and predict very quickly
-Fast, because logistic regression is a linear model, its decision function is a very simple linear function, so its computational complexity is low.
-Logistic regression model is easy to interpret, and the coefficient of the model can give the degree of influence of each feature on the model.
-This can be used in real business applications to help decision makers better understand the model's predictions.
-In addition, logistic regression models can handle large scale data well, because logistic regression models only need to dimension a small number of parameters to adapt well to a large number of parameters.
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
 # Results {#sec-results}
-Our results are summarized in @tbl-model-summary-tableLogistic, regression is a common classification algorithm used to predict binary classification problems.
-In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function.
-When interpreting the results of logistic regression models.
-Logistic regression models can provide coefficients (or weights) for each feature variable that represent the relative importance of the feature.
-The positive and negative symbols of the coefficient can tell us whether the feature has positive or negative influence on the target category, and the absolute value of the coefficient can map the importance of the feature to the target category.
-
-In this paper, we performed a logistic regression model from our cleaned dataset, which analysis 500 observations.
-Our focus of this paper was relationship of presidential candidate voted by individuals between the races (raceBlack, raceHispanic, raceMiddle Eastern, raceNative American, raceOther, raceTwo or more races, raceWhite) and the reference group, raceAsian.
 
@@
 ```
-The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump.
-When the coefficient values are negative, which means the voters decrease their support in Biden.
-Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden.
 
-From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same.
-The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden.
-Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
 # Discussion {#sec-Discussion}
@@
 ## Findings
-In this paper, the 2022 Cooperative Election Study (CES) was used for understanding the complexities of American electoral systems which was discussed in Section 2.
-In section 3, we applied a Bayesian logistic regression model to know if a person is likely to support Biden, based on their gender, race, and education status.
-In section 4, we discussed the summarization of the major results based on the research we did in Section 2 and 3.
-Summarization of our major results:
 
-1.Males are less likely to support Biden than Females,women most likely to vote for Biden,
-2.Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.
+## High income
 
-Throughout the discussion part, we will now provide detailed points of our results in the following sections.
+## Education
 
-## Males are less likely to support Biden than Females, women most likely to vote for Biden.
-
-Based on the analysis of @fig-vote, located under 2.6 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
-Throughout most of the race, 1 consistently has fewer votes than 2.
-Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy.
-This trend is very recognizable based on research: women are registered to vote in the U.S.
-at higher rates than men.
-In recent years, the number of women registered to vote in the U.S.
-has typically been about 10 million more than the number of men registered to vote.
-In every presidential election since 1980, the proportion of eligible female adults who voted has exceeded the proportion of eligible male adults who voted.
-In all presidential elections prior to 1980, the voter turnout rate for women was lower than the rate for men.
-The number of female voters has exceeded the number of male voters in every presidential election since 1964.
-
-## Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.
-
-Based on the analysis of @fig-vote, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, and Asian individuals are more likely to vote and show support for Biden.
-In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races.
-For example, Hispanic individuals have a total vote of 2481 individuals for Biden, however only 1210 individuals support and vote for Trump.
-This same trend can also be observed in races such as Middle Eastern, Hispanic, and Asian individuals.
-Additionally, in recent elections, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters.
-The gender gap in voter turnout rates is the largest for Black voters.
-In @tbl-model-summary-tableLogistic of our paper, we observe a negative coefficient for black people (−1.030) in support for Biden, indicating that Black people are displaying less support and fewer votes for Biden.
-The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump.
-When the coefficient values are negative, which means the voters decrease their support in Biden.
-Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden.
-Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s.
-Among Asian American/Pacific Islander voters, there is no consistent gender gap in voter turnout.
+## Gun ownership
 
 ## Application of Logistic Regression
-Logistic regression is also known as generalized linear regression model, and its form is basically the same as that of linear regression model.
-The biggest difference lies in their different dependent variables.
-If it is continuous, it is multiple linear regression.
-If it is a binomial distribution, it is Logistic regression.
-Although Logistic regression has the name "regression", it is actually a classification method, mainly used for binary classification problems (that is, there are only two outputs, each representing two categories), but also can handle multiple classification problems.
-Linear regression is used to predict continuous variables, whose value range is (- ", + "), while logistic regression model is used to predict categories.
-For example, using logistic regression model to predict whether an item belongs to class A or Class B essentially predicts the probability that the item belongs to class A or class B, and the value range of probability is 0~1.
-Therefore, it is not possible to predict the probability directly with the linear regression equation, which involves the Sigmoid function, which converts the values of the range (-∞, +∞) to the range (0,1).
 
 ## Linear Regression Model
-In summary, the essence of logistic regression model is to transform the linear regression model Q through a nonlinear Sigmoid function to obtain a probability value between 0 and 1.
-For binary classification problem (classification 0 and 1), the probability of predicting the classification as 1(or the classification with a larger value in the binary classification) can be calculated using the formula shown below.
-df has a total of about 7000 groups of historical data, of which about 2000 groups are lost customers, about 5000 groups are not lost customers will "whether to lose" as the target variable, other fields as characteristic variables, through some basic information and transaction records of a customer to predict whether he will lose, or judge the probability of loss.
 
 ## Model Building
-The training set is used to train the data and build the model, and the test set is used to check the effect of the model built after training.
-The purpose of dividing the training set and the test set is to evaluate the model, and to optimize the model through the test set.
-Dividing the training set and the test set is also, in part, to check for overfitting of the model.
 
 ## Weaknesses and Next Steps
-
-Logistic regression can only deal with linearly separable problems, and for nonlinear separable data, logistic regression will be poor.
-Logistic regression is sensitive to outliers, and if there are outliers in the data, the effect of logistic regression may be affected.
-Finally, logistic regression can usually only handle binary classification problems, and for multi-classification problems, some additional processing is required.
-If the sample size is insufficient or the features are too complex, logistic regression is prone to overfitting.
 

### 2024-04-01 scripts/02-data_cleaning.R

@@ -1,20 +1,16 @@
 #### Preamble ####
 # Purpose: Cleans the raw plane data by two observers to prepare for analysis. This includes filtering observations, recoding variables, and selecting relevant data.
-# Author: Yang Zhou, Yuean Wang, Dong Jun Yoon
-# Date: 14 March 2024
-# Contact: cocoyang.zhou@mail.utoronto.ca, yuean.wang@mail.utoronto.ca, dongjun.yoon@mail.utoronto.ca
+# Author: Yang Zhou
+# Date: 30 March 2024
+# Contact: cocoyang.zhou@mail.utoronto.ca
 # License: MIT
 
 
-#### Workspace setup ####
 library(tidyverse)
 
-#### Clean data ####
-raw_data <- read_csv("data/raw_datas/raw_datas.csv")
 
-cleaned_data <-
-  raw_data %>%
-  filter(votereg == 1, presvote20post %in% c(1, 2)) %>%
+cleaned_data <- raw_data |>
+  filter(votereg == 1, presvote20post %in% c(1, 2)) |>
   mutate(
     voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
     voted_for = as_factor(voted_for),
@@ -51,7 +47,7 @@ cleaned_data <-
       faminc_new == 14 ~ "$250,000 - $349,999",
       faminc_new == 15 ~ "$350,000 - $499,999",
       faminc_new == 16 ~ "$500,000 or more",
-      faminc_new == 17 ~ "Prefer not to say" 
+      faminc_new == 17 ~ "Prefer not to say" # Corrected duplicate value for '$500,000 or more' and 'Prefer not to say'
     ),
     faminc_new = factor(
       faminc_new,
@@ -89,9 +85,20 @@ cleaned_data <-
         "No one in the household owns a gun",
         "Not sure"
       )
+    ),
+    income_group = case_when(
+      faminc_new %in% c("Less than $10,000", "$10,000 - $19,999", "$20,000 - $29,999", "$30,000 - $39,999") ~ "Low",
+      faminc_new %in% c("$40,000 - $49,999", "$50,000 - $59,999", "$60,000 - $69,999", "$70,000 - $79,999") ~ "Middle",
+      faminc_new %in% c("$80,000 - $99,999", "$100,000 - $119,999", "$120,000 - $149,999", "$150,000 - $199,999") ~ "High",
[…]

### 2024-04-01 scripts/04-model.R

@@ -24,7 +24,7 @@ ces2022_reduced <-
 
 us_political_preferences <-
   stan_glm(
-    factor(voted_for) ~ educ + faminc_new + gunown,
+    factor(voted_for) ~ educ + income_group + gunown,
     data = ces2022_reduced ,
     family = binomial(link = "logit"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),

### 2024-04-02 paper/paper.qmd
update change

@@
 ## Source and Methodology
+The 2022 Cooperative Election Study (CES) [@main_data] was conducted by YouGov.
+In order to ensure the representativesness of the data, the survey utilized sampling methodology, matching process, weighting procedure.
 
 ## Sampling and Sampling Matching
+The survey interviewed 60,000 adults during two periods: pre-election from September 29 to November 8, 2022, and post-election from November 10 to December 15, 2022.
+YouGov employed matched random sample methodology for the sampling process.
+Sample matching is used to create representative samples from non-random pools of respondents and it is suitable for online survey.
+First,it will draw a random target population and then, it is going to select the matching respondents from the pool which matched with the target sample's characteristics.
+In order to replicate the target sample's attributes, YouGov uses proximity matching to calculates the likelihood or closeness between characteristics of the target samples; they will adjust the weight of variables when they need.
 
 ## Weightening
+The sample use two-stage weighting process to correct the imbalances between matched sample and target population.They use a weight method called entropy balancing, which focus on attributes including gender, race, education, age, and voting behavior
 

### 2024-04-02 paper/paper.qmd
update change

@@
 ## Weightening
-The sample use two-stage weighting process to correct the imbalances between matched sample and target population.They use a weight method called entropy balancing, which focus on attributes including gender, race, education, age, and voting behavior
+To correct the imbalance between the matched samples and the overarching target demographic, a two-phase weighting procedure is employed, ensuring the CES samples accurately mirror the population's diversity.
+The initial phase of this adjustment process involves entropy balancing, alongside iterative proportional fitting (often termed 'raking'), to align the sample with the population's demographic and political characteristics.
+This includes a comprehensive evaluation of variables and their interrelations.
+The approach guarantees that the common content of the survey represents each state accurately, incorporating adjustments for statewide electoral contests.
 
-## Vote Vaildation
+## Vote Validation
+Vote validation have been considered in the CES in order to verify the accuracy of the voting behaviors.
+The sample were matched to the TargetSmart database that include the registered voter responds.
+Only the records which have a high level of confidence could be matched.
+This process is helpful for identifying voters and the way they vote, such as absentee, early, and mail.Therefore CES can ensure the data is focused on voting behavior and accurately represent genuine voter engagement.
 
@@
 ```
-
+After installing `dataverse`[@dataverse], I use `get_dataframe_by_name` to analyze CES.
+I select four variables that most relevant to our topic, which are `votereg`, `presvote20post`, `educ`, `faminc_new`, `gunown`.
+`votereg` represents the voter registration status and only the voter who registered to vote would be considered.
+Besides, `presvote20post` represents the president that respondents vote in 2020 president election.
+I only consider the respond of Joe Biden and Donald Trump.
+`educ` means the education level of the respondents.
+In addition, `faminc_new` accounts for the family's annual income in 2021 year.
+`gunown` records the personal gun ownership by asking the respondent to answer whether they or anyone in their household own a gun.
 ```{r}

### 2024-04-02 scripts/02-data_cleaning.R
update change

@@ -7,10 +7,14 @@
 
 
 library(tidyverse)
+library(readr)
+library(here)
 
+# Assuming ces2022 is already read somewhere before this code
+# ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
 
-cleaned_data <- raw_data |>
-  filter(votereg == 1, presvote20post %in% c(1, 2)) |>
+cleaned_data <- ces2022 %>%
+  filter(votereg == 1, presvote20post %in% c(1, 2)) %>%
   mutate(
     voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
     voted_for = as_factor(voted_for),
@@ -30,47 +34,6 @@ cleaned_data <- raw_data |>
       "4-year",
       "Post-grad"
     )),
-    faminc_new = case_when(
-      faminc_new == 1 ~ "Less than $10,000",
-      faminc_new == 2 ~ "$10,000 - $19,999",
-      faminc_new == 3 ~ "$20,000 - $29,999",
-      faminc_new == 4 ~ "$30,000 - $39,999",
-      faminc_new == 5 ~ "$40,000 - $49,999",
-      faminc_new == 6 ~ "$50,000 - $59,999",
-      faminc_new == 7 ~ "$60,000 - $69,999",
-      faminc_new == 8 ~ "$70,000 - $79,999",
-      faminc_new == 9 ~ "$80,000 - $99,999",
-      faminc_new == 10 ~ "$100,000 - $119,999",
-      faminc_new == 11 ~ "$120,000 - $149,999",
-      faminc_new == 12 ~ "$150,000 - $199,999",
-      faminc_new == 13 ~ "$200,000 - $249,999",
-      faminc_new == 14 ~ "$250,000 - $349,999",
-      faminc_new == 15 ~ "$350,000 - $499,999",
-      faminc_new == 16 ~ "$500,000 or more",
-      faminc_new == 17 ~ "Prefer not to say" # Corrected duplicate value for '$500,000 or more' and 'Prefer not to say'
-    ),
-    faminc_new = factor(
-      faminc_new,
-      levels = c(
-        "Less than $10,000",
-        "$10,000 - $19,999",
-        "$20,000 - $29,999",
-        "$30,000 - $39,999",
-        "$40,000 - $49,999",
-        "$50,000 - $59,999",
-        "$60,000 - $69,999",
-        "$70,000 - $79,999",
-        "$80,000 - $99,999",
-        "$100,000 - $119,999",
[…]

### 2024-04-02 scripts/02-data_cleaning.R
update change

@@ -10,11 +10,9 @@ library(tidyverse)
 library(readr)
 library(here)
 
-# Assuming ces2022 is already read somewhere before this code
-# ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
 
-cleaned_data <- ces2022 %>%
-  filter(votereg == 1, presvote20post %in% c(1, 2)) %>%
+cleaned_data <- ces2022 |>
+  filter(votereg == 1, presvote20post %in% c(1, 2)) |>
   mutate(
     voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
     voted_for = as_factor(voted_for),
@@ -62,12 +60,12 @@ cleaned_data <- ces2022 %>%
       faminc_new == 10 ~ "High",
       faminc_new == 11 ~ "High",
       faminc_new == 12 ~ "High",
-      faminc_new >= 13 ~ "Very High" # Assuming codes 13 and above correspond to "$200,000 - $249,999", etc.
+      faminc_new >= 13 ~ "Very High" 
     )
-  ) %>%
+  ) |>
   mutate(
     income_group = factor(income_group, levels = c("Low", "Middle", "High", "Very High"))
-  ) %>%
+  ) |>
   select(voted_for, educ, income_group, gunown)
 
 # Save the cleaned data

### 2024-04-02 scripts/02-data_cleaning.R
upload change

@@ -7,8 +7,6 @@
 
 
 library(tidyverse)
-library(readr)
-library(here)
 
 
 cleaned_data <- ces2022 |>
@@ -32,6 +30,45 @@ cleaned_data <- ces2022 |>
       "4-year",
       "Post-grad"
     )),
+    faminc_new = case_when(
+      faminc_new == 1 ~ "Less than $10,000",
+      faminc_new == 2 ~ "$10,000 - $19,999",
+      faminc_new == 3 ~ "$20,000 - $29,999",
+      faminc_new == 4 ~ "$30,000 - $39,999",
+      faminc_new == 5 ~ "$40,000 - $49,999",
+      faminc_new == 6 ~ "$50,000 - $59,999",
+      faminc_new == 7 ~ "$60,000 - $69,999",
+      faminc_new == 8 ~ "$70,000 - $79,999",
+      faminc_new == 9 ~ "$80,000 - $99,999",
+      faminc_new == 10 ~ "$100,000 - $119,999",
+      faminc_new == 11 ~ "$120,000 - $149,999",
+      faminc_new == 12 ~ "$150,000 - $199,999",
+      faminc_new == 13 ~ "$200,000 - $249,999",
+      faminc_new == 14 ~ "$250,000 - $349,999",
+      faminc_new == 15 ~ "$350,000 - $499,999",
+      faminc_new == 16 ~ "$500,000 or more",
+      ),
+    faminc_new = factor(
+      faminc_new,
+      levels = c(
+        "Less than $10,000",
+        "$10,000 - $19,999",
+        "$20,000 - $29,999",
+        "$30,000 - $39,999",
+        "$40,000 - $49,999",
+        "$50,000 - $59,999",
+        "$60,000 - $69,999",
+        "$70,000 - $79,999",
+        "$80,000 - $99,999",
+        "$100,000 - $119,999",
+        "$120,000 - $149,999",
+        "$150,000 - $199,999",
+        "$200,000 - $249,999",
+        "$250,000 - $349,999",
+        "$350,000 - $499,999",
+        "$500,000 or more"
+      )
+    ),
     gunown = case_when(
       gunown == 1 ~ "Personally own a gun",
       gunown == 2 ~ "Someone in the household owns a gun",
@@ -48,25 +85,18 @@ cleaned_data <- ces2022 |>
       )
     ),
     income_group = case_when(
-      faminc_new == 1 ~ "Low",
-      faminc_new == 2 ~ "Low",
[…]

### 2024-04-03 paper/paper.qmd
update change

@@
 Besides, `presvote20post` represents the president that respondents vote in 2020 president election.
-I only consider the respond of Joe Biden and Donald Trump.
 `educ` means the education level of the respondents.
@@
 `gunown` records the personal gun ownership by asking the respondent to answer whether they or anyone in their household own a gun.
+However, for the raw data, there are six different answers, including choosing ,Joe Biden, Donald Trump, Jo Jorgensen, Howie Hawkins, other, and did not vote for President.
+I only consider the respond of Joe Biden and Donald Trump.
+Therefore, when I clean the data, I select the group of Joe Biden and Donald Trump.
+In addition, there are 6 different education level, ranging from no high school, high school graduate, some college, 2-year, 4-year, and post-grad.
+I care about all of the education level, so I take all of those types into consideration.
+Moreover, there are 16 ranges of family income and the differences between each range is 10,000.
+To simiplied the data, I classifed them into 4 different types.
+For the income group which Less than $10,000,  $10,000 - $19,999, $20,000 - $29,999, and $30,000 - $39,999 are defined as "Low" income group.
+For those who range from $40,000 to $79,999 can seem as  "Middle" income group.
+$80,000 to $199,999 can be considered as "High" income group.
+For the family earn $200,000 to $500,000 or more is very high income group.
 ```{r}

### 2024-04-03 scripts/02-data_cleaning.R

@@ -47,7 +47,7 @@ cleaned_data <- ces2022 |>
       faminc_new == 14 ~ "$250,000 - $349,999",
       faminc_new == 15 ~ "$350,000 - $499,999",
       faminc_new == 16 ~ "$500,000 or more",
-      ),
+    ),
     faminc_new = factor(
       faminc_new,
       levels = c(
@@ -96,6 +96,11 @@ cleaned_data <- ces2022 |>
     income_group = factor(income_group, levels = c("Low", "Middle", "High", "Very High"))
   ) |>
   select(voted_for, educ, income_group, gunown) 
+
+# Drop rows with any missing values in ces2022
+ces2022 <- ces2022 %>%
+  filter(complete.cases(.))
+
 
 # Save the cleaned data
 write_csv(cleaned_data, "data/analysis_data/analysis_data.csv")

### 2024-04-03 scripts/03-test_data.R

@@ -5,8 +5,6 @@
 # Contact: cocoyang.zhou@mail.utoronto.ca
 # License: MIT
 
-
-
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
@@ -19,13 +17,13 @@ test_that("Check class", {
   expect_type(cleaned_data$gunown, "character")
 })
 
-test_that("Check complete", {
-  expect_true(all(complete.cases(ces2022)))
-})
-
 
 test_that("Check variable",{
   expect_setequal(cleaned_data$voted_for, c("Biden", "Trump"))
   expect_setequal(cleaned_data$educ, c("No HS", "High school graduate", "Some college", "2-year", "4-year", "Post-grad"))
-  expect_setequal(unique(cleaned_data$faminc_new), c("Less than $10,000", "$10,000 - $19,999", "$20,000 - $29,999", "$30,000 - $39,999", "$40,000 - $49,999", "$50,000 - $59,999", "$60,000 - $69,999", "$70,000 - $79,999", "$80,000 - $99,999", "$100,000 - $119,999", "$120,000 - $149,999", "$150,000 - $199,999", "$200,000 - $249,999", "$250,000 - $349,999", "$350,000 - $499,999", "$500,000 or more", NA))
+  expect_setequal(unique(cleaned_data$faminc_new), c("Less than $10,000", "$10,000 - $19,999", "$20,000 - $29,999", "$30,000 - $39,999", "$40,000 - $49,999", "$50,000 - $59,999", "$60,000 - $69,999", "$70,000 - $79,999", "$80,000 - $99,999", "$100,000 - $119,999", "$120,000 - $149,999", "$150,000 - $199,999", "$200,000 - $249,999", "$250,000 - $349,999", "$350,000 - $499,999", "$500,000 or more"))
 })  
+
+test_that("Check complete", {
+  expect_true(all(complete.cases(ces2022)))
+})

### 2024-04-04 paper/paper.qmd
update change

@@
 For the family earn $200,000 to $500,000 or more is very high income group.
+
 ```{r}
 #| label: fig-vote
-#| fig-cap: The distribution of presidential preferences, by gender, and race
+#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
 #| echo: false
@@
 
-library(ggplot2)
-library(readr)
-library(here)
-
 ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
 
-ggplot(data = ces2022, aes(x = educ, fill = voted_for)) +
+ggplot(ces2022, aes(x = income_group, fill = voted_for)) +  
   geom_bar(position = "dodge") +  
@@
   ) +
-  facet_wrap(facets = vars(income_group)) +
-  theme_minimal(base_size = 14) +  
   labs(
-    x = "Education",
-    y = "Number of respondents",
+    x = "Income Level",  
+    y = "Number of Respondents",  
     fill = "Voted for"
@@
   scale_fill_brewer(palette = "Set1") +  
+  theme_minimal(base_size = 14) +  
   theme(
@@
   )
+
+```
+
+```{r}
+#| label: fig-vote
+#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
+#| echo: false
+#| warning: false
+#| message: false
+
+ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
+
+ggplot(ces2022, aes(x = educ, fill = voted_for)) +  
+  geom_bar(position = "dodge") +  
+  geom_text(
+    aes(label = ..count..),
+    stat = 'count',
+    position = position_dodge(width = 0.9),
+    vjust = -0.25,
+    color = "black",
+    size = 2.5
+  ) +
+  labs(
+    x = "Education Level",  
+    y = "Number of Respondents",  
+    fill = "Voted for"
+  ) +
+  coord_flip() +  
+  scale_fill_brewer(palette = "Set1") +  
+  theme_minimal(base_size = 14) +  
+  theme(
+    legend.position = "bottom", 
+    strip.text = element_text(size = 12)
+  )
+
+```
+```{r}
+#| label: fig-vote
+#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
+#| echo: false
+#| warning: false
+#| message: false
+
+ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
+
+# Generate the plot focusing on Personal Gun Ownership
+ggplot(ces2022, aes(x = gunown, fill = voted_for)) +  
+  geom_bar(position = "dodge") +  
+  geom_text(
+    aes(label = ..count..),
+    stat = 'count',
+    position = position_dodge(width = 0.9),
+    vjust = -0.25,
+    color = "black",
+    size = 2.5
+  ) +
+  labs(
+    x = "Personal Gun Ownership",  
+    y = "Number of Respondents",  
+    fill = "Voted for"
+  ) +
+  coord_flip() +  
+  scale_fill_brewer(palette = "Set1") +  
+  theme_minimal(base_size = 14) +  
+  theme(
+    legend.position = "bottom", 
+    strip.text = element_text(size = 12)
+  )
+
+```
+
+```{r}
+#| label: fig-vote
+#| fig-cap: The distribution of presidential preferences, by education, and income level
+#| echo: false
+#| warning: false
+#| message: false
+
+ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
+
+ggplot(ces2022, aes(x = educ, fill = voted_for)) +
+  geom_bar(position = "dodge") +  
+  geom_text(aes(label = ..count..), stat = "count", vjust = -0.25, position = position_dodge(0.9), color = "black", size = 2.5) +
+  facet_wrap(~income_group) +  
+  labs(x = "Education Level", y = "Number of Respondents", fill = "Vote") +
+  coord_flip() +  
+  theme_minimal() +  
+  scale_fill_brewer(palette = "Set1") +  
+  theme(legend.position = "bottom", strip.text = element_text(size = 12))  
+```
+
+```{r}
+#| label: fig-vote
+#| fig-cap: The distribution of presidential preferences, by education, and income level
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(ces2022, aes(x = income_group, fill = voted_for)) +
+  geom_bar(position = "fill") +
+  labs(x = "Income Group", y = "Proportion", fill = "Voted For") +
+  scale_fill_brewer(palette = "Set1") +
+  theme_minimal() +
+  theme(legend.position = "bottom")
+
 ```
@@
 
-Define $y_i$ is the political preference of the respondent and equal to 1 if Biden and 0 if Trump.
-Then $\mbox{education}_i$ is education level of the respondent and $\mbox{income}_i$ is the income of the respondent.
-
-The parameters can be derived utilizing the `stan_glm()` function.
-Practically, `rstanarm` transforms categorical variables into a set of binary indicators, leading to the estimation of numerous coefficients.
-To optimize computational efficiency, we will select a random subset of 500 data points for model fitting instead of using the entire dataset.
+Define $y_i$ is the political preference of the respondent, where $y_i$ equal to 1 indicates a preference for Biden and $y_i$ equal to 0 represent a preference for Trump.
+The predictors include $\mbox{education}_i$, which indicates the education level of the respondent and $\mbox{income}_i$ is the income level of the respondent.
+$\mbox{gunownership}_i$ is the state of whether individual or the people he/she knows own a gun.
 
@@
 y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
-\mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{education}_i +\beta_2 \times \mbox{income}_i\\
-\beta_0 &\sim \mbox{Normal}(0, 2.5)\\
-\beta_1 &\sim \mbox{Normal}(0, 2.5)\\
-\beta_2 &\sim \mbox{Normal}(0. 2.5)
+\mbox{logit}(\pi_i) &= \alpha + \beta \times \mbox{education}_i + \gamma \times \mbox{income}_i + \delta \times \mbox{gun}_i\\
+\alpha &\sim \mbox{Normal}(0, 2.5) \\
+\beta &\sim \mbox{Normal}(0, 2.5) \\
+\gamma &\sim \mbox{Normal}(0, 2.5) \\
+\delta &\sim \mbox{Normal}(0, 2.5)
 \end{align}
 
+I set up a logistic regression model within a Bayesian framework to estimate model parameters, which particularly focusing on binary outcome variables such as political preference.
+To be more specific, I utilize `stan_glm()` function from `rstanrm` [@rstanrm] package, which can handles categorical variables efficiently by converting them into binary indicators.
+In order to optimize computational efficiency, I use a random sample of 500 observations to fit the model.
+
 ## Model justification
+Logistic regression is designed for binary outcome variables,especially when the dependent variables indicates two categories, in this case, the dependent variables are voting for Biden(1) or Trump(0).
+This model can provide a straightforward method for estimating the probability for voting for a specific candidate based on its predictors, including education level, income level, and gun ownership.
+In addition, Logistic regression is an ideal choice for explaining how unit changes in predictors variables affect the dependent variables.
 

### 2024-04-04 paper/paper.qmd
update change

@@
 ```{r}
-#| label: fig-vote
-#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
+#| label: fig-income-vote
+#| fig-cap: The distribution of presidential preferences, by income level
 #| echo: false
@@
 ```{r}
-#| label: fig-vote
-#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
+#| label: fig-education-vote
+#| fig-cap: The distribution of presidential preferences, by education
 #| echo: false
@@
 ```{r}
-#| label: fig-vote
-#| fig-cap: The distribution of presidential preferences, by education, and gun ownership
+#| label: fig-gun-ownership-vote
+#| fig-cap: The distribution of presidential preferences, by gun ownership
 #| echo: false
@@
 ```{r}
-#| label: fig-vote
+#| label: fig-education-income-vote
 #| fig-cap: The distribution of presidential preferences, by education, and income level

### 2024-04-04 paper/paper.qmd
upload change

@@
 library(ggplot2)
+library(rstanarm)
 ```
@@
 
-## Source and Methodology
+## Source
 The 2022 Cooperative Election Study (CES) [@main_data] was conducted by YouGov.
@@
 
-## Sampling and Sampling Matching
+## Sampling
 The survey interviewed 60,000 adults during two periods: pre-election from September 29 to November 8, 2022, and post-election from November 10 to December 15, 2022.
@@
 # Results {#sec-results}
-
 ```{r}
@@
 
-library(rstanarm)
-
-us_political_preferences <-
+voting_preference <-
   readRDS(file = here::here("model/first_model.rds"))
@@
 #| label: tbl-model-summary-table
-#| tbl-cap: "Explanatory models of political preferences based on gender and race (n = 500)"
+#| tbl-cap: "Explanatory models of political preferences based on education, income and gun ownership (n = 500)"
 
@@
   list(
-    "Support Biden" = us_political_preferences
+    "Support Biden" = voting_preference
   ),
@@
 ```
+After conducting a logistic regression analysis on 500 samples, I summary the result in @tbl-model-summary-table.
+According to @Mustafa_2024, the coefficients of the model are referred to posterior means which provides a central tendency measure of parameter's posterior distribution.
+The coefficient represents the log odds of supporting Biden for the reference group while all other variables are held at their baseline values.
+I care about three predictors which are education level, income level, and gun ownership and focus on the relationship of political preference of different groups and their reference group.
+To be more specific, in terms of education level, the model interpret the relationship between the voters who are 4-year education, high school graduate, no high school, post graduate, some college and the reference group with a 2-year education.
+The reference group for income level is high income group range from $80,000 to $199,999 and its compared to other income group, including low income, middles income, and very high income.
+For the individual gun ownership, "no one in the household owns a gun" is the reference group.
+For example, the coefficient for voters with a 4-year education level is -0.251.
+This indicates that holding all other variables constant, the voters having a 4-year education compared to the reference group(2-year education) is associated with a slight decreases.
+However, I found that the coefficient -0.251 are not at least twist as large as the standard errors(0.391), which are the number shown in the bracket below the coefficient.
+This represents that it is not a statistically significant coefficient.
 
+## Income
+
+## Education
+
+## Gun ownership
 # Discussion {#sec-Discussion}

### 2024-04-04 scripts/04-model.R

@@ -22,7 +22,7 @@ ces2022_reduced <-
   analysis_data |> 
   slice_sample(n = 500)
 
-us_political_preferences <-
+voting_preference <-
   stan_glm(
     factor(voted_for) ~ educ + income_group + gunown,
     data = ces2022_reduced ,

### 2024-04-05 paper/paper.qmd
update change

@@
 ```{r}
-#| label: fig-education-vote
-#| fig-cap: The distribution of presidential preferences, by education
-#| echo: false
-#| warning: false
-#| message: false
-
-ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
-
-ggplot(ces2022, aes(x = educ, fill = voted_for)) +  
-  geom_bar(position = "dodge") +  
-  geom_text(
-    aes(label = ..count..),
-    stat = 'count',
-    position = position_dodge(width = 0.9),
-    vjust = -0.25,
-    color = "black",
-    size = 2.5
-  ) +
-  labs(
-    x = "Education Level",  
-    y = "Number of Respondents",  
-    fill = "Voted for"
-  ) +
-  coord_flip() +  
-  scale_fill_brewer(palette = "Set1") +  
-  theme_minimal(base_size = 14) +  
-  theme(
-    legend.position = "bottom", 
-    strip.text = element_text(size = 12)
-  )
-
-```
-```{r}
 #| label: fig-gun-ownership-vote
@@
 This indicates that holding all other variables constant, the voters having a 4-year education compared to the reference group(2-year education) is associated with a slight decreases.
-However, I found that the coefficient -0.251 are not at least twist as large as the standard errors(0.391), which are the number shown in the bracket below the coefficient.
-This represents that it is not a statistically significant coefficient.
+
+## Education
+According to @tbl-model-summary-table, the respondents who have high-school degree(1.337), no high school degree(1.131), and voter have some college degree (0.482) are more likely to vote for Biden, whereas, the people with 4-year education(-0.251), or post-graduate degree (-0.108) are less likely to vote for Biden.
 
 ## Income
-
-## Education
+The respondent with low income, ranging from less than $10,000 to $39,999, and very high income group, ranging from $200,000 to $500,000 or more, are less likely to vote for Biden.
+Their coefficients are −0.207 and −0.954 respectively.
+The middle income group is more likely to vote for Biden, ranging from $40,000 to $79,999.
 
 ## Gun ownership
+People own a gun(1.058) or know someone in the household owns a gun(0.280) have a larger likelihood to vote for Biden.
+
 # Discussion {#sec-Discussion}
+## Findings
+After I used a Bayesian logistic regression model to find the relationship between Biden support and the predictors, including education level, income level, and individual gun ownership, I conclude three main findings shown below:
+  1. People have higher education level is less likely to vote for Biden than those of lower education level
+  2. Middle income group tend to vote for Biden
+  3. The voters who own gun or know someone who own gun exhibit a higher propensity to vote for Biden
 
-## Findings
+## People have higher education level is less likely to vote for Biden than those of lower education level
+The summary data presented in @tbl-model-summary-table reveals a notable electoral dynamic: individuals possessing a four-year undergraduate degree or higher education credentials exhibit a lower propensity to support President Biden, in contrast to those whose highest educational attainment is a high school diploma or below, who show a marked tendency towards endorsing him.
+This pattern suggests that educational attainment may play a significant role in shaping political preferences, though it's important to acknowledge that a multitude of factors can influence an individual's voting decisions.
 
-## High income
+A critical consideration in unpacking these trends is the tax policy proposed by President Biden's administration, as outlined by @The_White_House_2024.
+The policy seeks to increase the marginal income tax rate to 39.6% for individuals whose annual earnings exceed $400,000.
+Notably, this income bracket is more likely to include individuals with advanced degrees.
+The people often command higher salaries because of their education level.
+Thus, the observed correlation between higher educational levels and diminished support for Biden might lead to considerations within this high earner regarding the potential impact of the proposed tax adjustments on their financial well-being.
 
-## Education
+Such concerns are not merely about the taxation but also about the perceived fairness and implications of these tax changes.
+High-earning individuals may worry about bearing a disproportionate tax burden.
+Additionally, this group might conduct the survey on the long-term economic impacts of higher taxes on investment, job creation, and overall economic growth.
 
-## Gun ownership
+Furthermore, this discussion highlights the complexity between education, income, and political ideology.
+While higher education often correlates with higher income, it also fosters exposure to diverse ideas and critical thinking skills that can influence political beliefs and policy preferences.
+Therefore, the relationship between education, income, and political preference might be complex.
 
-## Application of Logistic Regression
+## Middle income group tend to vote for Biden
+The analysis presented in @fig-income-vote compellingly demonstrates that Biden’s support base comprises significantly of middle and high-income groups, with the middle-income segment being particularly dominate.
+This trend is substantiated by data in @tbl-model-summary-table, which indicates positive correlation between support for Biden and belonging to the middle-income group.
+While there is no a specific analyses explicating the motivations behind this pattern, it is plausible to attribute this trend to Biden’s policy that directly benefit middle-income families, such as the enhancement of tax credits.
+According to @Parys, Biden has supported expanding tax credits for middle-income families, such as Children Tax Credit, which a measure designed to alleviate the financial burden of child-rearing for families.
+Middle income group could benefit from this policy.
+Under Biden's administration, according to @US_Department_of_the_Treasury_2022, there was an increased credit amount in 2021; the credit amount raised from $2,000 each child to $3,600 for each child who aged from 6 to 17.
+Unlike previous version, Biden support a fully refundable credit policy which aim to provide a direct financial assistance to families.
+This policy is really about helping middle-income families by giving them tax breaks and other benefits.
+The Biden administration is focusing on these families to help them with their money problems, which is why many of them support Biden.
 
-## Linear Regression Model
+## The voters who own gun or know someone who own gun exhibit a higher propensity to vote for Biden 
+The data presented in @tbl-model-summary-table reveals an interesting trend: individuals who own guns or are acquainted with gun owners exhibit a higher likelihood of supporting President Biden, despite he advocates more stringent gun control measures.
+Biden seeks to implement universal background checks, which called Bipartisan Background Checks Act.
+@Bipartisan_Background_Checks_Act aims to expand background check to cover all sales and transfers of weapons, including private transaction, online sales, and gun show sales.
 
-## Model Building
+This apparent paradox, where gun owners show support for a candidate known for promoting restrictive gun policies.
+It is plausible that gun owners, while cherishing their  rights, are equally concerned about the pervasive issue of gun violence concerns in the nation.
+Their support for Biden may because they recognize the measures such as universal background checks represent a balanced approach to regulate gun violence without infringing on the legitimate rights of the citizens to own firearms for personal security and recreational purposes.
 

### 2024-04-05 paper/paper.qmd
update change

@@
 In addition, by leveraging data from the 2022 CES, this paper delves into how variables such as education, income, and gun ownership serve as predictors for electoral choices, specifically the likelihood of voting for Biden or Trump.
+I used a logistic regression model to identify the likelihood.
 This analysis not only reveal the individual impact of these factors but also contributes to a broader understanding of the socio-economic and cultural impact of American electoral behavior.
 
-Based on our model, I found that individuals with higher incomes demonstrate a greater propensity to vote for Biden.
+Based on our model, I found that individuals with middle incomes demonstrate a greater propensity to vote for Biden.
 Additionally, elevated levels of personal gun ownership significantly correlate with an increased likelihood of supporting Biden.
@@
 To simiplied the data, I classifed them into 4 different types.
-For the income group which Less than $10,000,  $10,000 - $19,999, $20,000 - $29,999, and $30,000 - $39,999 are defined as "Low" income group.
+For the income group which less than $10,000,  $10,000 - $19,999, $20,000 - $29,999, and $30,000 - $39,999 are defined as "Low" income group.
 For those who range from $40,000 to $79,999 can seem as  "Middle" income group.
@@
 
+@fig-income-vote appears to be a bar chart displaying the number of respondents categorized by their income level, and which of the two candidates—Biden or Trump—they voted for.
+There are four income categories presented: Low, Middle, High, and Very High, with an additional category labeled "NA" that likely represents respondents whose income level was not available or not specified.
+
 ```{r}
@@
 ```
+In addition, @fig-gun-ownership-vote shows the number of respondents classified by their personal gun ownership status and which presidential candidate they voted for, either Biden or Trump.
+The categories of gun ownership are: "No one in the household owns a gun," "Personally own a gun," "Someone in the household owns a gun," and "NA" (which likely stands for data not available).
 
@@
 
-```{r}
-#| label: fig-vote
-#| fig-cap: The distribution of presidential preferences, by education, and income level
-#| echo: false
-#| warning: false
-#| message: false
-
-ggplot(ces2022, aes(x = income_group, fill = voted_for)) +
-  geom_bar(position = "fill") +
-  labs(x = "Income Group", y = "Proportion", fill = "Voted For") +
-  scale_fill_brewer(palette = "Set1") +
-  theme_minimal() +
-  theme(legend.position = "bottom")
-
-```
+@fig-education-income-vote combines the predictors of both income and education and displays the voting preferences (for Biden in red and for Trump in blue) of respondents broken down by their level of education (some college, post-grad, no high school (HS), high school graduate, 4-year degree, 2-year degree) and income level categories (high, very high, low, middle, and NA for data not available).
 
 ## Measurements 
+I will interpret how `educ`, `faminc_new`, and `gunown` be measured.
+Respondents were asked a series of questions regarding their voting preferences, demographic information, and other relevant factors such as education, income, and gun ownership.
+The survey conduct by online questionnaires and each variable is correspond to a question.
+To be more specific, in terms of `educ`, the respondents are asked to answer "What is the highest level of education you have completed?" and the respondents can choose their education level.
+The answers are categorized into "no high school," "high school graduate," "some college," "2-year degree," "4-year degree," and "post-grad."  However, the dataset fails to provide option for the respondents who graduate from secondary school or no education at all.
+`faminc_new` refer to the annual income for a family.
+People will be asked "Thinking back over the last year, what was your family's annual income?" The income ranges from less than $10,000 to more than $500,000.
+Some respondents might unwilling to disclose their actual income range.
+`gunown` indicates the status of gun ownership.
+In the course of gathering data on firearm ownership, the study must account for potential response biases.
+Specifically, individuals who may possess firearms unlawfully could exhibit a tendency to provide untruthful responses, driven by a fear of legal consideration.
 
@@
 ## Model set-up
-
 Define $y_i$ is the political preference of the respondent, where $y_i$ equal to 1 indicates a preference for Biden and $y_i$ equal to 0 represent a preference for Trump.
@@
 ## Weaknesses and Next Steps
+There are a few potential weaknesses for this paper.
+Firstly, I only conduct a logistic regression analysis on 500 samples for computational efficiency purpose.
+It is limited to reflect a representative sample, which might lead to a inaccurate conclusion on the population's attitudes and behaviors.
+
+In addition, the model can identify the relationship or correlation between different variables but it does not necessarily means causality.
+To build up a causal relationship require more experimental design.
+
+Moreover, select logistics model merely might fail to capture the overall interaction between predictors. In order to get a more detailed interpretation, some complex model might be helpful.
+
+For solving this limitation, the next steps can be firstly, expand the sample size.
+To design a research in longitudinal approach might also helpful for identify causality.
+Additionally, introduce other models to further ensure the accuracy and interpretability
+will also be useful.
 

### 2024-04-05 paper/paper.qmd
update changes

@@
 
-The Cooperative Election Study (CES)conduct a throughout survey encompassing a wide range of voter demographics and attitudes.CES collaborate with 60 researches teams to assembles sample comprising 60,000 cases.
+The Cooperative Election Study [@main_data]conduct a throughout survey encompassing a wide range of voter demographics and attitudes.CES collaborate with 60 researches teams to assembles sample comprising 60,000 cases.
 The cases are based on the survey of adult pariticipants in 2022 fall.
@@
 
-I will uses the programming language `R`[@citeR] to analyze the data.
-`dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm] will help me in the model and visualization part.
-
 # Data {#sec-data}
@@
 In order to ensure the representativesness of the data, the survey utilized sampling methodology, matching process, weighting procedure.
+
+I will uses the programming language `R`[@citeR] to analyze the data.
+`dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm] will help me in the model and visualization part.
 

### 2024-04-06 paper/datasheet.qmd
upload datasheet

@@
 author: 
-  - Dong Jun Yoon
-  - Yuean Wang
   - Yang Zhou
-thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
+thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-State.git.>"
 date: today
 date-format: long
-abstract: "The CES 2022 dataset, collected through an online survey by YouGov, encompasses 60,000 instances representing U.S.
-adult citizens' electoral behaviors, political opinions, and demographic characteristics.
-The instances are detailed and categorized by election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues.
-The dataset employs a matched random sampling methodology, with its representativeness validated through a two-stage weighting process involving entropy balancing and iterative proportional fitting.
-Preprocessing included sample matching, weighting, and vote validation, ensuring data quality and representativenes in order to avoid representative bias."
+abstract: "The CES 2022 dataset, gathered via an online survey conducted by YouGov, includes 60,000 data points that reflect the voting patterns, political views, and demographic profiles of American adults.
+This collection is organized into sections such as voting history, contextual background, demographics (for example, age, ethnicity, educational background), political leanings, and stances on a variety of policy matters.
+It utilizes a method of matched random sampling to ensure a broad representation, which is further corroborated by a dual-phase weighting mechanism that uses entropy balancing and iterative proportional fitting techniques.
+The preprocessing steps, which comprise sample matching, weighting, and verification of voting behavior, are meticulously carried out to maintain the integrity and representativeness of the data, thereby minimizing the risk of bias in representation."
 format: pdf
@@
 
-1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description
-    - The Cooperative Election Study (CES) aims to study how Americans perceive and hold their representatives accountable during elections.
-Besides, the study also interested in understanding their voting behavior and how their behavior be affected by political geography and social context.
-They study the group by capturing mass data across most of legislative constituencies.
-CES aims to fill the gap of understanding the American electoral process by analyzing congressional elections and national surveys.
+1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description*
+   -The Cooperative Election Study (CES) is dedicated to exploring American citizens' perceptions and accountability of their elected officials during elections.
+It delves into the intricacies of voting habits and the influence of political geography and societal factors on these behaviors.
+By gathering extensive data from a majority of legislative districts, the CES seeks to bridge the knowledge gap in the American electoral system through detailed analysis of congressional races and national polls.
 
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - The Cooperative Election Study. It form 62 research teams and organizations. 
+    -The CES initiative encompasses a collaborative effort of 62 research teams and organizations.
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
-    - CES is supported by the National Science Foundation (NSF). Award #2148907 is the associated grant it has. The grantors involve numerous teams and collaborations.
+    - The project receives backing from the National Science Foundation (NSF), under grant number 2148907.
+This grant supports the collaborative efforts of numerous teams and organizations involved in the study.
 4. *Any other comments?*
-    - Based on real data, the guide provide a deep research of understanding American electoral behavior and different impacts of social contexts on voting aspect.
-It might provide implication for analyzing the trend of American elections.
+    - None
 
@@
 Please provide a description.*
-	- The instances in CES 2022 dataset represent individual respondents attend in the survey, which designed to record various information related to electoral behaviour, political perspective and demographic characteristics.
-The The types of instances include election experience, contextual data, and demographic information.
+	- The CES 2022 dataset includes responses from individual participants who took part in the survey.
+This survey was structured to collect a wide range of information about voters' behaviors, political views, and demographic details.
+The data encompasses details on participants' voting experiences, the context of their electoral participation, and various demographic factors.
 
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- CES involves 60,000 cases. Those cases are based on the survey of adult pariticipants in 2022 fall.
+	- The CES study captured data from 60,000 respondents during the fall of 2022. These respondents were adult participants surveyed on a range of topics related to their electoral participation.
+
 3.
@@
 If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
-	- This dataset does not contain all possible instances. By contrast, it is more focus on drawn the sample from  a larger set of U.S. adult citizens.  
-	  The sampling method used by YouGov in the CES involved a matched random sampling method.
-This method begins with a count of the target population, which for general population studies includes all adults and is usually counted through a comprehensive survey such as the American Community Survey.
-CES then draws a random sample from that target population, called the target sample.
-	  The representativeness was validated by weighting procedures.
-This procedures aims to address any remaining imbalances among the matched sample.
-The sample is weighted to match the distribution of the frame across multiple demographic and political dimensions.
-The weighting process consists of two stages: entropy balancing, followed by iterative proportional fitting (tilting) of several key variables and their interactions.
+	- Instead of capturing every possible instances, the CES 2022 dataset prioritizes a selection drawn from a broader pool of adult citizens in the U.S.
+The approach utilized by YouGov for CES involves matched random sampling.
+This technique starts with identifying a target population count, typically encompassing all adults, often determined through extensive surveys like the American Community Survey.
+From this population, CES selects a random sample, referred to as the target sample.
+The accuracy of this sample's representativeness is enhanced through a two-stage weighting process.
+This process aims to correct any potential imbalances within the matched sample by adjusting the sample's distribution to align with the broader population across various demographic and political dimensions, utilizing entropy balancing and iterative proportional fitting for adjustments.
+
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
-	- It consists demographic information, political opinions and behaviors, electoral experiences, voter validation an device and participation information.
-In terms of political opinions, it includes respondents' political affiliations, voting president and their positions on various policy issues and political figures.
+	- The dataset encompasses a range of information, including demographic details, political beliefs and behaviors, electoral experiences, verification of voters, and data on device usage and participation.
+When it comes to political opinions, the dataset includes data on the political party affiliations of respondents, their choices for president, and their views on different policy matters and political figures.
+
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
 	- No.
+
 6.
@@
 This does not include intentionally removed information, but might include, for example, redacted text.*
-	- Vote file miss matching might be one of missing information from individual instances.
-The CES relies on matching respondent to outside voter files.
-There might be some chance that name, address, or other details are mismatch with respondent, leading to mismatch between voting status and respondent.
+  - The CES methodology includes matching respondents with external voter files, which can occasionally result in discrepancies.
+Errors in matching may arise from inconsistencies in names, addresses, or other personal information between the respondent and voter records, potentially leading to inaccuracies in correlating voting status with the individual respondent.
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	- CES 2022 dataset does not buil up a explicitly model relationship between individual instances.
-Each instance in the CES dataset represents a single respondent's survey answers, capturing their demographic details, political views, voting behavior, and other relevant information.
+	- The CES 2022 dataset is structured in such a way that it does not establish a direct model of relationships among individual responses.
+Instead, each entry in the dataset corresponds to the survey responses of an individual, encompassing a wide array of information including their demographic characteristics, political beliefs, voting actions, and other pertinent data.
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
@@
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- Random measurement error might be one of potential errors. For example, some respondents provides wrong answer, which might lead to a number of respondents being incorrectly categorized.
+	- Random measurement error is identified as a potential source of inaccuracies within the dataset.
+This may occur when respondents provide incorrect answers, inadvertently leading to some individuals being misclassified.
+
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- No, it does not link to external source.
-This dataset is mainly rely on survey collection of individual participants.Voter file matching might be an external consideration.
-Data for the CES 2022 study, including vote validation for all respondents, is archived and available at the Harvard University Dataverse.
-The restriction might be it does not include a specific restriction related to the TargetSmart database or other external resources used for voter file matching and verification are not detailed.
+	- The CES 2022 dataset primarily consists of survey responses and does not directly link to external sources.
+While voter file matching is a part of its methodology, specific details on external databases like TargetSmart used for this purpose are not extensively covered.
+However, comprehensive data from the CES 2022, including vote verification for participants, is stored and accessible through the Harvard University Dataverse.
+This indicates a lack of detailed disclosure concerning the use of external resources for voter file matching and validation.
 11.
@@
 If so, please provide a description.*
-	- The CES 2022 dataset consists primarily of structured survey data collected from respondents about their political views, behaviors, and demographic information.
-Such data is generally not subject to legal privileges such as doctor-patient confidentiality or confidentiality of legal communications.
+	- The CES 2022 collection is made up of methodically organized survey responses from individuals, shedding light on their political perspectives, activities, and demographic background.
+This type of data collection is typically free from the constraints of legal confidentiality agreements, such as those found between doctors and patients or in legal communications.
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- In terms of Racial and Sexual Agreement, it might be offensive for the respondent, especially when the question design in a way that might present bias.
+	- Survey questions relating to racial and sexual categories may be perceived as insensitive or biased by some respondents, potentially raising concerns about the manner in which these topics are approached.
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- There are lots of sub-population in the dataset. 
-	1)Gender: The dataset categorizes respondents into "Man", "Woman", "Non-binary", and "Other", allowing for gender-based analyses.
-	2)Race: The dataset categorizes respondents into "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other"
-	3)Education: Respondents' highest education levels are detailed, ranging from no high school diploma ("No HS") to postgraduate degrees
-	4)Political Affiliation: The dataset records respondents' party affiliation, including "Democrat", "Republican", and "Independent/Other".
-	5)Age: The dataset provide age range  (e.g., 18-29, 30-44, 45-64, 65 and over).
+	- Several sub-population in the dataset. 
+  1)Gender: The dataset categorizes respondents into "Man", "Woman", "Non-binary", and "Other"
+  2)Education:ranging from no high school diploma ("No HS") to postgraduate degrees
+  3)Age: age range from 18 to 65 and over 65
+  4)Race:"White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other"
+  5)Political Affiliation: including "Democrat", "Republican", and "Independent/Other".
 
@@
 If so, please describe how.*
-	- No, all the dataset is anomymize.
+	- No
 15.
@@
 If so, please provide a description.*
-	- Yes, it includes race, sexual orientation, religious, political opinion, transgender status, health data and so on.
-For example, respondents are asked to answer their sexual orientation, with options including heterosexual/straight, lesbian/gay, bisexual, and others.
+	- The dataset indeed covers a broad spectrum of personal attributes including race, sexual orientation, religious beliefs, political views, transgender status, and health information.
+For instance, questions about sexual orientation offer choices like heterosexual/straight, lesbian/gay, bisexual, among others.
 16. *Any other comments?*
@@
 If so, please describe how.*
-	- The data associated with each instance in the CES 2022 was primarily acquired through survey responses reported directly by the subjects.
-The survey was conducted online by YouGov and involved a methodology known as sample matching.The target population is first counted and then a representative sample is selected from a non-randomly selected group of respondents.
-  - Regarding the data segments concerning voter validation, the process involved aligning individual entries with the TargetSmart database, which contains records of U.S.
-registered voters.
-This alignment aimed to confirm the accuracy of survey respondents' claims about their voter registration and their actual voting activity in both the primary and general elections of 2022.
+	- Information for each entry in the CES 2022 dataset was mainly derived from direct survey inputs from participants.
+These surveys, managed by YouGov online, utilized a technique known as sample matching to select a subset of respondents that representatively reflects the broader target population.
+Additionally, parts of the dataset focusing on confirming voter registration details involved cross-referencing responses with the TargetSmart database, holding information on registered voters in the U.S., to verify the accuracy of participants' reported voter registration and activity in the elections.
+
 2.
@@
 How were these mechanisms or procedures validated?*
-	- The CES 2022 data was collected through an online survey conducted by YouGov.
-They employed  "sample matching" methodology, which fit with online access panels.This method identify available respondents who are very similar in terms of measured characteristics to each member of the target sample.
-The total distance is calculated as the weighted sum of these individual distances on all attributes, and the weights can be adjusted for variables that are important to the study.
-This approach allows matched samples to closely represent the characteristics of the target population.
+	- The CES 2022 utilized an online survey mechanism for data collection, implemented by YouGov.
+The "sample matching" methodology was applied, aligning with online panel access.
+This process involves selecting respondents who share similar attributes with the target demographic, using a formula that considers the aggregate differences across various characteristics.
+Adjustments are made to ensure the sample accurately mirrors the target population's traits.
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- The CES 2022 dataset's sampling strategy employed YouGov’s matched random sample methodology. 
+	- YouGov's methodology for creating the CES 2022 dataset involved a matched random sample approach, aiming to accurately represent the target population by matching survey participants to a predetermined demographic profile.
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- . The CES involved 60 parties and research teams. The dataset does not provide specific details on how individuals be compensated.
+	- The CES project was a collaborative effort involving 60 research teams and organizations.
+Specific details about participant compensation or involvement terms were not disclosed within the dataset's documentation.
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- Collected over two time frame: the first period is the pre-election data collection occurred from September 29 to November 8, 2022,and the second period is  post-election data was gathered from November 10 to December 15, 2022.The timeframe is relevant to survey participants about their opinions, voting intention in 2022 election.
+	- The data collection for CES 2022 spanned two distinct periods: the pre-election phase from September 29 to November 8, 2022, and the post-election phase from November 10 to December 15, 2022.
+This timeline was specifically chosen to capture respondents' perspectives and intentions related to the 2022 elections accurately.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	-  The dataset does not provide explicit details regarding any ethical review processes.
+	-  No specific information regarding the conduct of ethical review processes for the CES 2022 dataset has been provided.
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- The data for the 2022 Cooperative Election Study (CES) was collected directly from individuals through a survey conducted over the internet by YouGov.
+	- Data collection for the 2022 Cooperative Election Study (CES) was achieved through a survey administered by YouGov, which using the internet to reach respondents directly.
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	-Yes, because it is conducteddirectly from individuals through a survey conducted by YouGov over the internet.
-Cooperative Election Study (CES) or provide the exact language used in the notification.
+	Yes, the CES data was indeed gathered directly from respondents via an online survey facilitated by YouGov, confirming the method of data collection.
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- The individuals participating in the 2022 Cooperative Election Study (CES) did provide their consent for data collection.The respondent will be asked if they agree to attend in the survey by inquired "Consent to participate: Do you agree to participate in the study?" The exact language used to request consent, is straightforward.
+	- Participants in the 2022 CES explicitly gave their consent to be part of the study.
+They were presented with a clear inquiry about their willingness to participate, framed as "Consent to participate: Do you agree to participate in the study?" to ensure informed consent was obtained.
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- The dataset does not provide specific information about whether individuals were given a mechanism to revoke their consent after agreeing to participate in the 2022 Cooperative Election Study (CES) or for certain uses of their data.
+	- There is no detailed information within the dataset regarding whether participants in the 2022 CES had the option to withdraw their consent at any stage after initial agreement or to restrict certain uses of their data.
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- The provided CES Guide 2022 document does not specifically describe conducting a data protection impact analysis. It emphasizes on on the methodology, sample matching, data collection, 
+	- No, it focuses on outlining the study's methodology, including sample matching and the procedures for collecting data.
 12. *Any other comments?*
@@
 If not, you may skip the remaining questions in this section.*
-	- Yes, CES involves some data preprocessing, cleaning, and labeling to make sure the quality of the data.
-The descriptions have been included in the sampling methodology, matching procedures, and weighting processes.
-CES done 3 things, which are sampling and sample matching, weighting, and vote validation.To be more specific, in order to correct for any residual imbalances between the matched sample and the target population, the CES data was weight through 2 steps.
-First, using entropy balancing to match the distributions of the frame on key demographic variables (age, gender, education, race, etc.), and then using iterative proportional fitting ("raking") on additional variables (like voter registration status and 2020 Presidential vote choice) to further refine the representativeness of the sample.
+	- Yes, the CES undertakes several data preprocessing steps to ensure high data quality, including cleaning and labeling.
+These steps are detailed within the methodology section, focusing on sampling, sample matching, weighting, and voter validation.
+Specifically, to address any discrepancies between the sampled group and the broader target population, the CES employs a two-step weighting process.
+Initially, entropy balancing is used to align the sample's distribution with key demographic factors such as age, gender, education, and race.
+Following this, iterative proportional fitting, or "raking," is applied to other variables like voter registration status and 2020 Presidential vote preferences, further enhancing the sample's representativeness.
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- The CES Guide 2022 does not explicitly mention whether the "raw" data save in addition to the preprocessed/cleaned/labeled data.
+	- No.
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
@@
 	- Yes, it will.
-It indicated that the data for the Cooperative Election Study (CES) 2022 is available at the Harvard University Dataverse.
-This can be seem as the dataset is accessible to third parties outside of the institutions directly involved in the creation of the dataset, such as Harvard University and YouGov.
+It indicated that the data for the Cooperative Election Study (CES) 2022.
+It is accessable in the Harvard University Dataverse.
+it is available to external parties beyond those directly involved in its survey.
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- The Cooperative Election Study (CES) 2022 will be distributed through the Harvard University Dataverse.
-This distribution method ensures that the dataset is accessible for academic and research purposes.
-The DOI for the Cooperative Election Study Common Content 2022 is https://doi.org/10.7910/DVN/PR4L8P,
+	- The CES 2022 dataset is shared via the Harvard University Dataverse, in order to ensure academic and research can access the data. The dataset's DOI is https://doi.org/10.7910/DVN/PR4L8P.
+
 3. *When will the dataset be distributed?*
-	- Dataset is distributed in two period: first, on March 20, 2023.
-It included the CES 2022 Common Content, which is the data collected that is common across all participating research teams.The second period is on September 8, 2023, it included vote validation for all respondents, enhancing the dataset's utility for electoral research by verifying the voting behavior reported by the survey participants.
+	- The distribution of the dataset occurs in two phases.
+Firstly, on March 20, 2023, the CES 2022 Common Content was released, encompassing data uniformly collected by all the contributing research teams.
+Subsequently, on September 8, 2023, vote validation data for all participants was added, significantly augmenting the dataset's value for election studies by confirming the accuracy of the voting behavior reported by survey respondents.electoral research by verifying the voting behavior reported by the survey participants.
 4.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- TBD
+	- No.
 7. *Any other comments?*
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- The dataset for the CES 2022 is maintained and hosted by the Harvard University Dataverse.
+	-The Harvard University Dataverse support the dataset.
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- People can directly contact The Harvard University Dataverse platform.
+	- People can contact the dataset via the Harvard University Dataverse platform.
 3. *Is there an erratum? If so, please provide a link or other access point.*
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- The guide does not provide detail information about update.
+	- Do not have specific information about that.
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- The CES Guide 2022 does not provide specific information regarding limits on the retention of data associated with the instances.
+	-  Do not have specific information about that.
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- The guide does not discuss about the policies regarding the support, hosting, or maintenance of older versions of the dataset.
+	-  Do not have specific information about that.
 7.
@@
 If so, please provide a description.*
-	- The guide does not include a explicit mechanism for others to extend to the dataset.
+	-  Do not have specific information about that.
 8. *Any other comments?*

### 2024-04-06 paper/paper.qmd
upload datasheet

@@
 ---
-title: "Demographic Groups with Stronger Biden Support in the Election Race'"
+title: "Modeling Voter Preference Dynamics: Education, Income, and Gun Ownership in the 2020 US Presidential Election"
 author: 

### 2024-04-06 paper/paper.qmd
update change

@@
 
+##Appendix
+**Motivation**
+
+1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description*
+   -The Cooperative Election Study (CES) is dedicated to exploring American citizens' perceptions and accountability of their elected officials during elections.
+It delves into the intricacies of voting habits and the influence of political geography and societal factors on these behaviors.
+By gathering extensive data from a majority of legislative districts, the CES seeks to bridge the knowledge gap in the American electoral system through detailed analysis of congressional races and national polls.
+
+2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
+    -The CES initiative encompasses a collaborative effort of 62 research teams and organizations.
+3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
+    - The project receives backing from the National Science Foundation (NSF), under grant number 2148907.
+This grant supports the collaborative efforts of numerous teams and organizations involved in the study.
+4. *Any other comments?*
+    - None
+
+**Composition**
+
+1.
+*What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)?
+Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)?
+Please provide a description.*
+	- The CES 2022 dataset includes responses from individual participants who took part in the survey.
+This survey was structured to collect a wide range of information about voters' behaviors, political views, and demographic details.
+The data encompasses details on participants' voting experiences, the context of their electoral participation, and various demographic factors.
+
+2. *How many instances are there in total (of each type, if appropriate)?*
+	- The CES study captured data from 60,000 respondents during the fall of 2022. These respondents were adult participants surveyed on a range of topics related to their electoral participation.
+
+3.
+*Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set?
+If the dataset is a sample, then what is the larger set?
+Is the sample representative of the larger set (for example, geographic coverage)?
+If so, please describe how this representativeness was validated/verified.
+If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
+	- Instead of capturing every possible instances, the CES 2022 dataset prioritizes a selection drawn from a broader pool of adult citizens in the U.S.
+The approach utilized by YouGov for CES involves matched random sampling.
+This technique starts with identifying a target population count, typically encompassing all adults, often determined through extensive surveys like the American Community Survey.
+From this population, CES selects a random sample, referred to as the target sample.
+The accuracy of this sample's representativeness is enhanced through a two-stage weighting process.
+This process aims to correct any potential imbalances within the matched sample by adjusting the sample's distribution to align with the broader population across various demographic and political dimensions, utilizing entropy balancing and iterative proportional fitting for adjustments.
+
+4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
+	- The dataset encompasses a range of information, including demographic details, political beliefs and behaviors, electoral experiences, verification of voters, and data on device usage and participation.
+When it comes to political opinions, the dataset includes data on the political party affiliations of respondents, their choices for president, and their views on different policy matters and political figures.
+
+5. *Is there a label or target associated with each instance? If so, please provide a description.*
+	- No.
+
+6.
+*Is any information missing from individual instances?
+If so, please provide a description, explaining why this information is missing (for example, because it was unavailable).
+This does not include intentionally removed information, but might include, for example, redacted text.*
+  - The CES methodology includes matching respondents with external voter files, which can occasionally result in discrepancies.
+Errors in matching may arise from inconsistencies in names, addresses, or other personal information between the respondent and voter records, potentially leading to inaccuracies in correlating voting status with the individual respondent.
+7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
+	- The CES 2022 dataset is structured in such a way that it does not establish a direct model of relationships among individual responses.
+Instead, each entry in the dataset corresponds to the survey responses of an individual, encompassing a wide array of information including their demographic characteristics, political beliefs, voting actions, and other pertinent data.
+8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
+	- No.
+9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
+	- Random measurement error is identified as a potential source of inaccuracies within the dataset.
+This may occur when respondents provide incorrect answers, inadvertently leading to some individuals being misclassified.
+
+10.
+*Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)?
+If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer?
+Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
+	- The CES 2022 dataset primarily consists of survey responses and does not directly link to external sources.
+While voter file matching is a part of its methodology, specific details on external databases like TargetSmart used for this purpose are not extensively covered.
+However, comprehensive data from the CES 2022, including vote verification for participants, is stored and accessible through the Harvard University Dataverse.
+This indicates a lack of detailed disclosure concerning the use of external resources for voter file matching and validation.
+11.
+*Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)?
+If so, please provide a description.*
+	- The CES 2022 collection is made up of methodically organized survey responses from individuals, shedding light on their political perspectives, activities, and demographic background.
+This type of data collection is typically free from the constraints of legal confidentiality agreements, such as those found between doctors and patients or in legal communications.
+12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
+	- Survey questions relating to racial and sexual categories may be perceived as insensitive or biased by some respondents, potentially raising concerns about the manner in which these topics are approached.
+13.
+*Does the dataset identify any sub-populations (for example, by age, gender)?
+If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
+	- Several sub-population in the dataset. 
+  1)Gender: The dataset categorizes respondents into "Man", "Woman", "Non-binary", and "Other"
+  2)Education:ranging from no high school diploma ("No HS") to postgraduate degrees
+  3)Age: age range from 18 to 65 and over 65
+  4)Race:"White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other"
+  5)Political Affiliation: including "Democrat", "Republican", and "Independent/Other".
+
+14.
+*Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset?
+If so, please describe how.*
+	- No
+15.
+*Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)?
+If so, please provide a description.*
+	- The dataset indeed covers a broad spectrum of personal attributes including race, sexual orientation, religious beliefs, political views, transgender status, and health information.
+For instance, questions about sexual orientation offer choices like heterosexual/straight, lesbian/gay, bisexual, among others.
+16. *Any other comments?*
+	- No
+
+**Collection process**
+
+1.
+*How was the data associated with each instance acquired?
+Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)?
+If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified?
+If so, please describe how.*
+	- Information for each entry in the CES 2022 dataset was mainly derived from direct survey inputs from participants.
+These surveys, managed by YouGov online, utilized a technique known as sample matching to select a subset of respondents that representatively reflects the broader target population.
+Additionally, parts of the dataset focusing on confirming voter registration details involved cross-referencing responses with the TargetSmart database, holding information on registered voters in the U.S., to verify the accuracy of participants' reported voter registration and activity in the elections.
+
+2.
+*What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)?
+How were these mechanisms or procedures validated?*
+	- The CES 2022 utilized an online survey mechanism for data collection, implemented by YouGov.
+The "sample matching" methodology was applied, aligning with online panel access.
+This process involves selecting respondents who share similar attributes with the target demographic, using a formula that considers the aggregate differences across various characteristics.
+Adjustments are made to ensure the sample accurately mirrors the target population's traits.
+3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
+	- YouGov's methodology for creating the CES 2022 dataset involved a matched random sample approach, aiming to accurately represent the target population by matching survey participants to a predetermined demographic profile.
+4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
+	- The CES project was a collaborative effort involving 60 research teams and organizations.
+Specific details about participant compensation or involvement terms were not disclosed within the dataset's documentation.
+5.
+*Over what timeframe was the data collected?
+Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)?
+If not, please describe the timeframe in which the data associated with the instances was created.*
+	- The data collection for CES 2022 spanned two distinct periods: the pre-election phase from September 29 to November 8, 2022, and the post-election phase from November 10 to December 15, 2022.
+This timeline was specifically chosen to capture respondents' perspectives and intentions related to the 2022 elections accurately.
+6.
+*Were any ethical review processes conducted (for example, by an institutional review board)?
+If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
+	-  No specific information regarding the conduct of ethical review processes for the CES 2022 dataset has been provided.
+7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
+	- Data collection for the 2022 Cooperative Election Study (CES) was achieved through a survey administered by YouGov, which using the internet to reach respondents directly.
+8.
+*Were the individuals in question notified about the data collection?
+If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
+	Yes, the CES data was indeed gathered directly from respondents via an online survey facilitated by YouGov, confirming the method of data collection.
+9.
+*Did the individuals in question consent to the collection and use of their data?
+If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
+	- Participants in the 2022 CES explicitly gave their consent to be part of the study.
+They were presented with a clear inquiry about their willingness to participate, framed as "Consent to participate: Do you agree to participate in the study?" to ensure informed consent was obtained.
+10.
+*If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses?
+If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
+	- There is no detailed information within the dataset regarding whether participants in the 2022 CES had the option to withdraw their consent at any stage after initial agreement or to restrict certain uses of their data.
+11.
+*Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted?
+If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
+	- No, it focuses on outlining the study's methodology, including sample matching and the procedures for collecting data.
+12. *Any other comments?*
+	- No
+
+**Preprocessing/cleaning/labeling**
+
+1.
+*Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)?
+If so, please provide a description.
+If not, you may skip the remaining questions in this section.*
+	- Yes, the CES undertakes several data preprocessing steps to ensure high data quality, including cleaning and labeling.
+These steps are detailed within the methodology section, focusing on sampling, sample matching, weighting, and voter validation.
+Specifically, to address any discrepancies between the sampled group and the broader target population, the CES employs a two-step weighting process.
+Initially, entropy balancing is used to align the sample's distribution with key demographic factors such as age, gender, education, and race.
+Following this, iterative proportional fitting, or "raking," is applied to other variables like voter registration status and 2020 Presidential vote preferences, further enhancing the sample's representativeness.
+2.
+*Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)?
+If so, please provide a link or other access point to the "raw" data.*
+	- No.
+3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
+	- No.
+4. *Any other comments?*
+	- No.
+
+**Uses**
+
+1. *Has the dataset been used for any tasks already? If so, please provide a description.*
+	- The CES Guide 2022 does not provide specific examples of tasks for which the dataset has already been used.
+2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
+	- The CES Guide 2022 does not explicitly mention a repository that links to paper.
+3. *What (other) tasks could the dataset be used for?*
+	- There are multiple task that the dataset can be used for. For example, to analyze voting behavior and study the impact of socioeconomic factor on political outcome.
+4.
+*Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?
+For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)?
+If so, please provide a description.
+Is there anything a dataset consumer could do to mitigate these risks or harms?*
+	- Yes.The methodology section details efforts to create a representative sample and address potential biases through sample matching, weighting, and vote validation in order to avoid representation bias.The customer can ensure all research complies with applicable laws, ethical standards, and best practices for data privacy and protection.
+5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
+	- No.
+6. *Any other comments?*
+	- No.
+
+**Distribution**
+
+1.
+*Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created?
+If so, please provide a description.*
+	- Yes, it will.
+It indicated that the data for the Cooperative Election Study (CES) 2022.
+It is accessable in the Harvard University Dataverse.
+it is available to external parties beyond those directly involved in its survey.
+2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
+	- The CES 2022 dataset is shared via the Harvard University Dataverse, in order to ensure academic and research can access the data. The dataset's DOI is https://doi.org/10.7910/DVN/PR4L8P.
+
+3. *When will the dataset be distributed?*
+	- The distribution of the dataset occurs in two phases.
+Firstly, on March 20, 2023, the CES 2022 Common Content was released, encompassing data uniformly collected by all the contributing research teams.
+Subsequently, on September 8, 2023, vote validation data for all participants was added, significantly augmenting the dataset's value for election studies by confirming the accuracy of the voting behavior reported by survey respondents.electoral research by verifying the voting behavior reported by the survey participants.
+4.
+*Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)?
+If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
+	- No.
+5.
+*Have any third parties imposed IP-based or other restrictions on the data associated with the instances?
+If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
+	- No.
+6.
+*Do any export controls or other regulatory restrictions apply to the dataset or to individual instances?
+If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
+	- No.
+7. *Any other comments?*
+	- No.
+
+**Maintenance**
+
+1. *Who will be supporting/hosting/maintaining the dataset?*
+	-The Harvard University Dataverse support the dataset.
+2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
+	- People can contact the dataset via the Harvard University Dataverse platform.
+3. *Is there an erratum? If so, please provide a link or other access point.*
+	- No
+4.
+*Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)?
+If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
+	- Do not have specific information about that.
+5.
+*If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)?
+If so, please describe these limits and explain how they will be enforced.*
+	-  Do not have specific information about that.
+6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
+	-  Do not have specific information about that.
+7.
+*If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so?
+If so, please provide a description.
+Will these contributions be validated/verified?
+If so, please describe how.
+If not, why not?
+Is there a process for communicating/distributing these contributions to dataset consumers?
+If so, please provide a description.*
+	-  Do not have specific information about that.
+8. *Any other comments?*
+	- No
+
 \newpage
